#### Descriptive Summaries  {.tabset .tabset-fade .tabset-pills}

Biomarkers are summarised below on the basis of the primary classification of Pulmonary Embolism status.  Histograms of the distribution within each classification (`PE`, `No PE` or `Exclude`) are displayed followed by a table showing the number, mean, standard deviation, median and inter-quartile range and the minimum and maximum values observed.  No formal statistical tests for differences are shown since these are provided by the Logistic Regression analyses.

**IMPORTANT** Because of the exclusion of a large amount of Thrombin biomarker data by virtue of individuals (N = `r dplyr::filter(master$biomarker_exclusions_clean, exclude.anti.coag == 'Yes') %>% nrow()`) having received anti-coagulants prior to their blood sample being taken there is a large degree of variation in the y-axis scale of the following histograms.

##### Prothombin (Time)

```{r  demographics_biomarker_prothombin_time_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, prothombin.time, first.st) %>%
    mutate(first.st = as.character(first.st),
           first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                                  no  = first.st)) %>%
    ggplot(aes(x    = prothombin.time,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Prothombin Time (sec)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Prothombin (Time)') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Prothombin (Time) by Primary Classification')

```

##### Clauss Fibrinogen

```{r  demographics_biomarker_clauss_fibrinogen_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, clauss.fibrinogen, first.st) %>%
    mutate(first.st = as.character(first.st),
           first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                                  no  = first.st)) %>%
    ggplot(aes(x    = clauss.fibrinogen,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Clauss Fibrinogen (g/l)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Clauss Fibrinogen') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Clauss Fibrinogen by Primary Classification')

```

##### D-Dimer (Innovan)

```{r  demographics_biomarker_ddimer_innovan_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, ddimer.innovan, first.st) %>%
    mutate(first.st = as.character(first.st),
           first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                                  no  = first.st)) %>%
    ggplot(aes(x    = ddimer.innovan,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('D-Dimer (mg/l)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.biomarkers$first.st, Measurement == 'D-Dimer (Innovan)') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of D-Dimer (Innovan) by Primary Classification')

```

##### D-Dimer (ELISA)

```{r  demographics_biomarker_ddimer_elisa_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, ddimer.elisa, first.st) %>%
    mutate(first.st = as.character(first.st),
           first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                                  no  = first.st)) %>%
    ggplot(aes(x    = ddimer.elisa,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('D-Dimer (ng/l)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.biomarkers$first.st, Measurement == 'D-Dimer (ELISA)') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of D-Dimer (ELISA) by Primary Classification')

```

##### Thrombin Generation (Lag Time)

```{r  demographics_biomarker_thrombin_generation_lag_time_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, thrombin.generation.lag.time, first.st) %>%
    mutate(first.st = as.character(first.st),
           first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                                  no  = first.st)) %>%
    ggplot(aes(x    = thrombin.generation.lag.time,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Thrombin Generation - Lag Time (min)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Thrombin Generation (Lag Time)') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Thrombin Generation (Lag Time)')

```

##### Thrombin Generation (Endogenous Potential)

```{r  demographics_biomarker_thrombin_generation_endogenous_potential_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, thrombin.generation.endogenous.potential, first.st) %>%
    mutate(first.st = as.character(first.st),
           first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                                  no  = first.st)) %>%
    ggplot(aes(x    = thrombin.generation.endogenous.potential,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Thrombin Generation Endogenous Potential (nM x min)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Thrombin Generation (Endogenous Potential)') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Thrombin Generation (Endogenous Potential)')

```

##### Thrombin Generation (Time to Peak)

```{r  demographics_biomarker_thrombin_generation_time_to_peak_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, thrombin.generation.time.to.peak, first.st) %>%
    mutate(first.st = as.character(first.st),
           first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                                  no  = first.st)) %>%
    ggplot(aes(x    = thrombin.generation.time.to.peak,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Thrombin Generation - Time to Peak (min)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Thrombin Generation (Time to Peak)') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Thrombin Generation (Time to Peak)')

```

##### Thrombin Generation (Peak)

```{r  demographics_biomarker_thrombin_generation_peak_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, thrombin.generation.peak, first.st) %>%
    mutate(first.st = as.character(first.st),
           first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                                  no  = first.st)) %>%
    ggplot(aes(x    = thrombin.generation.peak,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Thrombin Generation - Peak (nM)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Thrombin Generation (Peak)') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Thrombin Generation (Peak)')

```

##### Plasmin Antiplasmin

```{r  demographics_biomarker_plasmin_antiplasmin_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, plasmin.antiplasmin, first.st) %>%
    mutate(first.st = as.character(first.st),
           first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                                  no  = first.st)) %>%
    ggplot(aes(x    = plasmin.antiplasmin,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Plasmin Antiplasmin (sec)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Plasmin (Antiplasmin)') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Plasmin Antiplasmin')

```


##### Natriuertic Peptide

```{r  demographics_biomarker_natriuertic_peptide_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = FALSE}
dplyr::select(dipep, natriuertic.peptide, first.st) %>%
    mutate(first.st = as.character(first.st),
           first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                                  no  = first.st)) %>%
    ggplot(aes(x    = natriuertic.peptide,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Natriuertic Peptide (pg/ml)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Natriuertic Peptide') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Natriuertic Peptide')

```

##### MRproANP

```{r  demographics_biomarker_mrproanp_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = FALSE}
dplyr::select(dipep, mrproanp, first.st) %>%
    mutate(first.st = as.character(first.st),
           first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                                  no  = first.st)) %>%
    ggplot(aes(x    = mrproanp,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('MRproANP (pmol/l)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.biomarkers$first.st, Measurement == 'MRproANP') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'MRproANP')

```
