#### Descriptive Summaries  {.tabset .tabset-fade .tabset-pills}

Biomarkers are summarised below on the basis of the primary classification of Pulmonary Embolism status.  Histograms of the distribution within each classification (`PE`, `No PE` or `Exclude`) are displayed followed by a table showing the number, mean, standard deviation, median and inter-quartile range and the minimum and maximum values observed.  No formal statistical tests for differences are shown since these are provided by the Logistic Regression analyses.

**IMPORTANT** Because of the exclusion of a large amount of Thrombin biomarker data by virtue of individuals (N = `r dplyr::filter(master$biomarker_exclusions_clean, exclude.anti.coag == 'Yes') %>% nrow()`) having received anti-coagulants prior to their blood sample being taken there is a large degree of variation in the y-axis scale of the following histograms.


##### Aprothombin

```{r  demographics_biomarker_aprothombin_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot       = 'Aprothombin (min)',
                      title.class           = 'Primary Classification',
                      first.st, aprothombin)
to.plot$histogram
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Aprothombin') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Summary of Aprothombin by Primary Classification')
to.plot$scatter

```

##### Prothombin (Time)

```{r  demographics_biomarker_prothombin_time_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot       = 'Prothombin (min)',
                      title.class           = 'Primary Classification',
                      first.st, prothombin.time)
to.plot$histogram
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Prothombin (Time)') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Summary of Prothombin (Time) by Primary Classification')
to.plot$scatter

```

##### Clauss Fibrinogen

```{r  demographics_biomarker_clauss_fibrinogen_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot       = 'Clauss Fibrinogen (g/l)',
                      title.class           = 'Primary Classification',
                      first.st, clauss.fibrinogen)
to.plot$histogram
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Clauss Fibrinogen') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Summary of Clauss Fibrinogen by Primary Classification')
to.plot$scatter

```

##### D-Dimer (Innovan)

```{r  demographics_biomarker_ddimer_innovan_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot       = 'D-Dimer - Innovan (mg/l)',
                      title.class           = 'Primary Classification',
                      first.st, ddimer.innovan)
to.plot$histogram
dplyr::filter(summary.biomarkers$first.st, Measurement == 'D-Dimer (Innovan)') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Summary of D-Dimer (Innovan) by Primary Classification')
to.plot$scatter

```

##### D-Dimer (ELISA)

```{r  demographics_biomarker_ddimer_elisa_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot       = 'D-Dimer - ELISA (ng/l)',
                      title.class           = 'Primary Classification',
                      first.st, ddimer.elisa)
to.plot$histogram
dplyr::filter(summary.biomarkers$first.st, Measurement == 'D-Dimer (ELISA)') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Summary of D-Dimer (ELISA) by Primary Classification')
to.plot$scatter

```

##### Thrombin Generation (Lag Time)

```{r  demographics_biomarker_thrombin_generation_lag_time_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot       = 'Thrombin Generation - Lag Time (min)',
                      title.class           = 'Primary Classification',
                      first.st, thrombin.generation.lag.time)
to.plot$histogram
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Thrombin Generation (Lag Time)') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Thrombin Generation (Lag Time)')
to.plot$scatter

```

##### Thrombin Generation (Endogenous Potential)

```{r  demographics_biomarker_thrombin_generation_endogenous_potential_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot       = 'Thrombin Generation - Endogenous Potential (min)',
                      title.class           = 'Primary Classification',
                      first.st, thrombin.generation.endogenous.potential)
to.plot$histogram
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Thrombin Generation (Endogenous Potential)') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Thrombin Generation (Endogenous Potential)')
to.plot$scatter

```

##### Thrombin Generation (Time to Peak)

```{r  demographics_biomarker_thrombin_generation_time_to_peak_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot       = 'Thrombin Generation - Time to Peak (min)',
                      title.class           = 'Primary Classification',
                      first.st, thrombin.generation.time.to.peak)
to.plot$histogram
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Thrombin Generation (Time to Peak)') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Thrombin Generation (Time to Peak)')
to.plot$scatter

```

##### Thrombin Generation (Peak)

```{r  demographics_biomarker_thrombin_generation_peak_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot       = 'Thrombin Generation - Peak (nM)',
                      title.class           = 'Primary Classification',
                      first.st, thrombin.generation.peak)
to.plot$histogram
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Thrombin Generation (Peak)') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Thrombin Generation (Peak)')
to.plot$scatter

```

##### Plasmin Antiplasmin

```{r  demographics_biomarker_plasmin_antiplasmin_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot       = 'Plasmin Antiplasmin (sec)',
                      title.class           = 'Primary Classification',
                      first.st, plasmin.antiplasmin)
to.plot$histogram
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Plasmin (Antiplasmin)') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Plasmin Antiplasmin')
to.plot$scatter

```


##### Natriuertic Peptide

```{r  demographics_biomarker_natriuertic_peptide_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot       = 'Natriuertic Peptide (pg/ml)',
                      title.class           = 'Primary Classification',
                      first.st, natriuertic.peptide)
to.plot$histogram
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Natriuertic Peptide') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Natriuertic Peptide')
to.plot$scatter

```

##### MRproANP

```{r  demographics_biomarker_mrproanp_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot       = 'MRproANP (pmol/l)',
                      title.class           = 'Primary Classification',
                      first.st, mrproanp)
to.plot$histogram
dplyr::filter(summary.biomarkers$first.st, Measurement == 'MRproANP') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'MRproANP')
to.plot$scatter

```
