##### Descriptive Summaries (Excluding Anti-Coagulation) {.tabset .tabset-fade .tabset-pills}

Biomarkers are summarised below on the basis of the primary classification of Pulmonary Embolism status.  Histograms of the distribution within each classification (`PE`, `No PE` or `Exclude`) are displayed followed by a table showing the number, mean, standard deviation, median and inter-quartile range and the minimum and maximum values observed.  No formal statistical tests for differences are shown since these are provided by the Logistic Regression analyses.

**IMPORTANT** Because of the exclusion of a large amount of Thrombin biomarker data by virtue of individuals (N = `r dplyr::filter(master$biomarker_exclusions_clean, exclude.anti.coag == 'Yes') %>% nrow()`) having received anti-coagulants prior to their blood sample being taken there is a large degree of variation in the y-axis scale of the following histograms.

```{r  demographics_biomarker_excl_anti_coag_summary, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
summary.biomarkers <- list()
summary.biomarkers$first.st <- dipep_summarise(df           = dipep,
                      	                  grouping     = 'first.st',
                      	                  group.as.col = TRUE,
                                          exclude               = NULL,
                                          exclude.non.recruited = TRUE,
                                          exclude.dvt           = TRUE,
                                          exclude.anti.coag     = TRUE,
                      	                  prothombin.time, aptt, clauss.fibrinogen, ddimer.innovance,
                                          thrombin.generation.lag.time, thrombin.generation.endogenous.potential,
                                          thrombin.generation.peak, thrombin.generation.time.to.peak,
                                          ddimer.elisa, plasmin.antiplasmin, prothrombin.fragments,
                                          tissue.factor, troponin,
                                          nppb, mrproanp)
summary.biomarkers$second.st <- dipep_summarise(df           = dipep,
                                                grouping     = 'second.st',
                                                group.as.col = TRUE,
                                                exclude               = NULL,
                                                exclude.non.recruited = TRUE,
                                                exclude.dvt           = TRUE,
                                                exclude.anti.coag     = TRUE,
                                                prothombin.time, aptt, clauss.fibrinogen, ddimer.innovance,
                                                thrombin.generation.lag.time, thrombin.generation.endogenous.potential,
                                                thrombin.generation.peak, thrombin.generation.time.to.peak,
                                                ddimer.elisa, plasmin.antiplasmin, prothrombin.fragments,
                                                tissue.factor, troponin,
                                                nppb, mrproanp)
summary.biomarkers$third.st <- dipep_summarise(df           = dipep,
                                               grouping     = 'third.st',
                                               group.as.col = TRUE,
                                               exclude               = NULL,
                                               exclude.non.recruited = TRUE,
                                               exclude.dvt           = TRUE,
                                               exclude.anti.coag     = TRUE,
                                               prothombin.time, aptt, clauss.fibrinogen, ddimer.innovance,
                                               thrombin.generation.lag.time, thrombin.generation.endogenous.potential,
                                               thrombin.generation.peak, thrombin.generation.time.to.peak,
                                               ddimer.elisa, plasmin.antiplasmin, prothrombin.fragments,
                                               tissue.factor, troponin,
                                               nppb, mrproanp)
summary.biomarkers$fourth.st <- dipep_summarise(df           = dipep,
                                                grouping     = 'fourth.st',
                                                group.as.col = TRUE,
                                                exclude               = NULL,
                                                exclude.non.recruited = TRUE,
                                                exclude.dvt           = TRUE,
                                                exclude.anti.coag     = TRUE,
                                                prothombin.time, aptt, clauss.fibrinogen, ddimer.innovance,
                                                thrombin.generation.lag.time, thrombin.generation.endogenous.potential,
                                                thrombin.generation.peak, thrombin.generation.time.to.peak,
                                                ddimer.elisa, plasmin.antiplasmin, prothrombin.fragments,
                                                tissue.factor, troponin,
                                                nppb, mrproanp)

```

###### APTT

```{r  demographics_biomarker_excl_anti_coag_aptt_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      exclude.anti.coag     = TRUE,
                      title.to.plot         = 'aptt (min)',
                      title.class           = 'Primary Classification',
                      first.st, aptt)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.biomarkers$first.st, Measurement == 'APTT') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Summary of APTT by Primary Classification')

```

###### Prothombin (Time)

```{r  demographics_biomarker_excl_anti_coag_prothombin_time_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      exclude.anti.coag     = TRUE,
                      title.to.plot       = 'Prothombin (min)',
                      title.class           = 'Primary Classification',
                      first.st, prothombin.time)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Prothombin (Time)') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Summary of Prothombin (Time) by Primary Classification')

```

###### Clauss Fibrinogen

```{r  demographics_biomarker_excl_anti_coag_clauss_fibrinogen_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      exclude.anti.coag     = TRUE,
                      title.to.plot       = 'Clauss Fibrinogen (g/l)',
                      title.class           = 'Primary Classification',
                      first.st, clauss.fibrinogen)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Clauss Fibrinogen') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Summary of Clauss Fibrinogen by Primary Classification')

```

###### D-Dimer (Innovance)

```{r  demographics_biomarker_excl_anti_coag_ddimer_innovan_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      exclude.anti.coag     = TRUE,
                      title.to.plot       = 'D-Dimer - Innovance (mg/l)',
                      title.class           = 'Primary Classification',
                      first.st, ddimer.innovance)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.biomarkers$first.st, Measurement == 'D-Dimer (Innovance)') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Summary of D-Dimer (Innovance) by Primary Classification')

```

###### D-Dimer (ELISA)

```{r  demographics_biomarker_excl_anti_coag_ddimer_elisa_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      exclude.anti.coag     = TRUE,
                      title.to.plot       = 'D-Dimer - ELISA (ng/l)',
                      title.class           = 'Primary Classification',
                      first.st, ddimer.elisa)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.biomarkers$first.st, Measurement == 'D-Dimer (ELISA)') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Summary of D-Dimer (ELISA) by Primary Classification')

```

###### Thrombin Generation (Lag Time)

```{r  demographics_biomarker_excl_anti_coag_thrombin_generation_lag_time_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      exclude.anti.coag     = TRUE,
                      title.to.plot       = 'Thrombin Generation - Lag Time (min)',
                      title.class           = 'Primary Classification',
                      first.st, thrombin.generation.lag.time)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Thrombin Generation (Lag Time)') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Thrombin Generation (Lag Time)')

```

###### Thrombin Generation (Endogenous Potential)

```{r  demographics_biomarker_excl_anti_coag_thrombin_generation_endogenous_potential_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      exclude.anti.coag     = TRUE,
                      title.to.plot       = 'Thrombin Generation - Endogenous Potential (min)',
                      title.class           = 'Primary Classification',
                      first.st, thrombin.generation.endogenous.potential)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Thrombin Generation (Endogenous Potential)') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Thrombin Generation (Endogenous Potential)')

```

###### Thrombin Generation (Time to Peak)

```{r  demographics_biomarker_excl_anti_coag_thrombin_generation_time_to_peak_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      exclude.anti.coag     = TRUE,
                      title.to.plot       = 'Thrombin Generation - Time to Peak (min)',
                      title.class           = 'Primary Classification',
                      first.st, thrombin.generation.time.to.peak)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Thrombin Generation (Time to Peak)') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Thrombin Generation (Time to Peak)')

```

###### Thrombin Generation (Peak)

```{r  demographics_biomarker_excl_anti_coag_thrombin_generation_peak_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      exclude.anti.coag     = TRUE,
                      title.to.plot       = 'Thrombin Generation - Peak (nM)',
                      title.class           = 'Primary Classification',
                      first.st, thrombin.generation.peak)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Thrombin Generation (Peak)') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Thrombin Generation (Peak)')

```

###### Plasmin Antiplasmin

```{r  demographics_biomarker_excl_anti_coag_plasmin_antiplasmin_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      exclude.anti.coag     = TRUE,
                      title.to.plot       = 'Plasmin Antiplasmin (sec)',
                      title.class           = 'Primary Classification',
                      first.st, plasmin.antiplasmin)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Plasmin (Antiplasmin)') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Plasmin Antiplasmin')

```


###### NPPB

```{r  demographics_biomarker_excl_anti_coag_nppb_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      exclude.anti.coag     = TRUE,
                      title.to.plot       = 'NPPB (pg/ml)',
                      title.class           = 'Primary Classification',
                      first.st, nppb)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.biomarkers$first.st, Measurement == 'NPPB') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'NPPB')

```

###### MRproANP

```{r  demographics_biomarker_excl_anti_coag_mrproanp_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      exclude.anti.coag     = TRUE,
                      title.to.plot       = 'MRproANP (pmol/l)',
                      title.class           = 'Primary Classification',
                      first.st, mrproanp)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.biomarkers$first.st, Measurement == 'MRproANP') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'MRproANP')

```

###### Tissue Factor

```{r  demographics_biomarker_excl_anti_coag_tissue_factor_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      exclude.anti.coag     = TRUE,
                      title.to.plot       = 'Tissue Factor',
                      title.class           = 'Primary Classification',
                      first.st, tissue.factor)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.biomarkers$first.st, Measurement == 'Tissue Factor') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Tissue Factor')

```

###### PF 1 + 2

```{r  demographics_biomarker_excl_anti_coag_pf12_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      exclude.anti.coag     = TRUE,
                      title.to.plot       = 'PF 1 + 2',
                      title.class           = 'Primary Classification',
                      first.st, prothrombin.fragments)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.biomarkers$first.st, Measurement == 'PF 1 + 2') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'PF 1 + 2')

```
