```{r ddimer_prep, , echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 10, results = 'markup', eval = TRUE}
ukoss.ddimer.nonmissing <- dplyr::filter(dipep, group == 'Diagnosed PE' & !is.na(d.dimer)) %>% nrow()
ukoss.ddimer.missing    <- dplyr::filter(dipep, group == 'Diagnosed PE' & is.na(d.dimer))  %>% nrow()
ukoss.n <- dplyr::filter(dipep, group == 'Diagnosed PE') %>% nrow()

```

D-Dimer assays from the multitude of independant hospitals/laboratories from which the UKOSS cohort (N = `r ukoss.ddimer.nonmissing`) are combined with the assays performed on samples from the Suspected Pulmonary Emoblism cohort at Kings College London by [Kiran Parmar](mailto:kiran.parmar@kcl.ac.uk).  It is important to bear in mind that of the total `r ukoss.n` individuals included in the study `r ukoss.ddimer.missing` are missing data for any form of D-Dimer assay in the data provided by UKOSS.

**NB** This is far from ideal, assays on the samples from Suspected Pulmonary Embolism were standardised because as mentioned in @murphy2015 *D-dimer concentrations are instrument-dependent; assays vary because the D-dimer analyte is not a simple structure with a uniform composition*.  It has been suggested that the laboratory specific reference ranges are used to standardise measurements across all sites, but to date such reference ranges are not available so the data is analysed "as is" and this caveat serves as a warning against over-interpretting the results.

There are two sets of results as Kiran performed D-Dimer assays using two different methods/kits, ELISA and Innovance.  The various UKOSS assays have therefore been combined with both and the analyses repeated.


```{r ddimer_summary, , echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 10, results = 'markup', eval = FALSE}
ddimer.pooled.all <- dipep_summarise(df           = dipep,
                                     grouping     = 'first.st',
                                     group.as.col = TRUE,
                                     exclude               = NULL,
                                     exclude.non.recruited = TRUE,
                                     exclude.dvt           = TRUE,
                                     exclude.anti.coag     = FALSE,
                                     exclude.missing       = FALSE,
                                     ddimer.elisa.pooled, ddimer.innovance.pooled)
ddimer.pooled.excl.anti.coag <- dipep_summarise(df           = dipep,
                                                grouping     = 'first.st',
                                                group.as.col = TRUE,
                                                exclude               = NULL,
                                                exclude.non.recruited = TRUE,
                                                exclude.dvt           = TRUE,
                                                exclude.anti.coag     = TRUE,
                                                exclude.missing       = FALSE,
                                                ddimer.elisa.pooled, ddimer.innovance.pooled)
```


###### ELISA {.tabset .tabset-fade .tabset-pills}

*NB* No standardisation has been performed because reference ranges for UKOSS D-Dimer measurements are not available.
####### All

```{r ddimer_summary_elisa_all, , echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 10, results = 'markup', eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      exclude.anti.coag     = FALSE,
                      exclude.missing       = FALSE,
                      title.to.plot         = 'D-Dimer (ELISA) - Pooled',
                      title.class           = 'Primary Classification',
                      first.st, ddimer.elisa.pooled)
to.plot$histogram
to.plot$scatter
rm(to.plot)
dplyr::filter(summary.biomarkers.all$first.st, Measurement == 'D-Dimer (ELISA) - Pooled') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Summary of D-Dimer (ELISA) and UKOSS assays by Primary Classification')


```

```{r ddimer_logistic_elisa_all, , echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 10, results = 'markup', eval = TRUE}
biomarker.all$ddimer.elisa.pooled$tidied %>%
    kable(caption   = 'Logistic Regression for D-Dimer (ELISA) pooled with UKOSS D-Dimer (Mixed)',
          col.names = c('Term', 'Estimate', 'Std Error', 'Statistic', 'P-value', 'Lower 95% CI', 'Upper 95% CI', 'Model'))
biomarker.all$ddimer.elisa.pooled$roc

```

####### Excluding those on Anti-Coagulants

```{r ddimer_summary_elisa_excl_anti_coag, , echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 10, results = 'markup', eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      exclude.anti.coag     = TRUE,
                      exclude.missing       = FALSE,
                      title.to.plot         = 'D-Dimer (ELISA) - Pooled',
                      title.class           = 'Primary Classification',
                      first.st, ddimer.elisa.pooled)
to.plot$histogram
to.plot$scatter
rm(to.plot)
dplyr::filter(summary.biomarkers.excl.anti.coag$first.st, Measurement == 'D-Dimer (ELISA) - Pooled') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Summary of D-Dimer (ELISA) and UKOSS assays by Primary Classification')


```

```{r ddimer_logistic_elisa_excl_anti_coag, , echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 10, results = 'markup', eval = TRUE}
biomarker.excl.anti.coag$ddimer.elisa.pooled$tidied %>%
    kable(caption   = 'Logistic Regression for D-Dimer (ELISA) pooled with UKOSS D-Dimer (Mixed)',
          col.names = c('Term', 'Estimate', 'Std Error', 'Statistic', 'P-value', 'Lower 95% CI', 'Upper 95% CI', 'Model'))
biomarker.excl.anti.coag$ddimer.elisa.pooled$roc

```


###### Innovance {.tabset .tabset-fade .tabset-pills}

*NB* No standardisation has been performed because reference ranges for UKOSS D-Dimer measurements are not available.

####### All

```{r ddimer_summary_innovance_all, , echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 10, results = 'markup', eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      exclude.anti.coag     = FALSE,
                      exclude.missing       = FALSE,
                      title.to.plot         = 'D-Dimer (INNOVANCE) - Pooled',
                      title.class           = 'Primary Classification',
                      first.st, ddimer.innovance.pooled)
to.plot$histogram
to.plot$scatter
rm(to.plot)
dplyr::filter(summary.biomarkers.all$first.st, Measurement == 'D-Dimer (Innovance) - Pooled') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Summary of D-Dimer (Innovance) and UKOSS assays by Primary Classification')


```

```{r ddimer_logistic_innovance_all, , echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 10, results = 'as.is', eval = TRUE}
biomarker.all$ddimer.innovance.pooled$tidied %>%
    kable(caption   = 'Logistic Regression for D-Dimer (Innovance) pooled with UKOSS D-Dimer (Mixed)',
          col.names = c('Term', 'Estimate', 'Std Error', 'Statistic', 'P-value', 'Lower 95% CI', 'Upper 95% CI', 'Model'))
biomarker.all$ddimer.innovance.pooled$roc

```

####### Excluding those on Anti-Coagulants

```{r ddimer_summary_innovance_excl_anti_coag, , echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 10, results = 'markup', eval = TRUE}
to.plot <- dipep_plot(df      = dipep,
                      exclude = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      exclude.anti.coag     = FALSE,
                      exclude.missing       = FALSE,
                      title.to.plot         = 'D-Dimer (INNOVANCE) - Pooled',
                      title.class           = 'Primary Classification',
                      first.st, ddimer.innovance.pooled)
to.plot$histogram
to.plot$scatter
rm(to.plot)
dplyr::filter(summary.biomarkers.excl.anti.coag$first.st, Measurement == 'D-Dimer (Innovance) - Pooled') %>%
    dplyr::select(-Measurement) %>%
        kable(caption = 'Summary of D-Dimer (Innovance) and UKOSS assays by Primary Classification')


```

```{r ddimer_logistic_innovance_excl_anti_coag, , echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.width = 10, fig.height = 10, results = 'as.is', eval = TRUE}
biomarker.excl.anti.coag$ddimer.innovance.pooled$tidied %>%
    kable(caption   = 'Logistic Regression for D-Dimer (Innovance) pooled with UKOSS D-Dimer (Mixed)',
          col.names = c('Term', 'Estimate', 'Std Error', 'Statistic', 'P-value', 'Lower 95% CI', 'Upper 95% CI', 'Model'))
biomarker.excl.anti.coag$ddimer.innovance.pooled$roc

```
