The full results of the univariable logistic regression are presented below.  For each variable a summry of the logistic regression model is shown followed by four diagnostic plots and then the individual ROC curve for the variable.

#### Age (Continuous)
```{r child = 'logistic/age.Rmd', eval = TRUE}
```

#### Age (Categorical)
```{r child = 'logistic/age.cat.Rmd', eval = TRUE}
```

#### BMI (Continuous)
```{r child = 'logistic/bmi.Rmd', eval = TRUE}
```

#### BMI (Categorical)
```{r child = 'logistic/bmi.cat.Rmd', eval = TRUE}
```

#### Diastolic Blood Pressure (Continuous)
```{r child = 'logistic/bp.diastolic.Rmd', eval = TRUE}
```

#### Diastolic Blood Pressure (Categorical)
```{r child = 'logistic/bp.diastolic.cat.Rmd', eval = TRUE}
```

#### Systolic Blood Pressure (Continuous)
```{r child = 'logistic/bp.systolic.Rmd', eval = TRUE}
```

#### Systolic Blood Pressure (Categorical)
**NB** No one had abnormal systolic blood pressure and as the outcome was invariant it is impossible to perform any form of regression.
```{r child = 'logistic/bp.systolic.cat.Rmd', eval = FALSE}
```

#### Heart Rate (Continuous)
```{r child = 'logistic/heart.rate.Rmd', eval = TRUE}
```

#### Heart Rate (Categorical)
```{r child = 'logistic/heart.rate.cat.Rmd', eval = TRUE}
```

#### Oxygen Saturation (Continuous)
```{r child = 'logistic/o2.saturation.Rmd', eval = TRUE}
```

#### Oxygen Saturation (Categorical)
```{r child = 'logistic/o2.saturation.cat.Rmd', eval = TRUE}
```

#### Respiratory Rate (Continuous)
```{r child = 'logistic/respiratory.rate.Rmd', eval = TRUE}
```

#### Respiratory Rate (Categorical)
```{r child = 'logistic/respiratory.rate.cat.Rmd', eval = TRUE}
```

#### History of IV Drug Use
```{r child = 'logistic/history.iv.drug.Rmd', eval = TRUE}
```

#### Family History of Thrombosis
```{r child = 'logistic/history.thrombosis.Rmd', eval = TRUE}
```

#### History of Varicose Veins
```{r child = 'logistic/history.veins.Rmd', eval = TRUE}
```

#### Previous Pregnancy Problems
```{r child = 'logistic/prev.preg.problem.Rmd', eval = TRUE}
```

#### Problems with Current Pregnancy
```{r child = 'logistic/this.pregnancy.problems.Rmd', eval = TRUE}
```

#### Multiple Pregnancy
```{r child = 'logistic/multiple.preg.Rmd', eval = TRUE}
```

#### Trimester
```{r child = 'logistic/trimester.Rmd', eval = TRUE}
```

#### One or more Pregnancy > 24 weeks
```{r child = 'logistic/pregnancies.over.Rmd', eval = TRUE}
```

#### Known Thrombophilia
```{r child = 'logistic/thrombo.Rmd', eval = TRUE}
```

#### History of Thrombosis
```{r child = 'logistic/thrombosis.Rmd', eval = TRUE}
```
