### Univariable Logistic Regression  {.tabset .tabset-fade .tabset-pills}

The full results of the univariable logistic regression are presented below.  For each variable a summry of the logistic regression model is shown followed by four diagnostic plots and then the individual ROC curve for the variable.

#### Age (Continuous)
```{r child = 'logistic/age.Rmd', eval = TRUE}
```

#### Age (Categorical)
```{r child = 'logistic/age.cat.Rmd', eval = TRUE}
```

#### BMI (Continuous)
```{r child = 'logistic/bmi.Rmd', eval = TRUE}
```

#### BMI (Categorical)
```{r child = 'logistic/bmi.cat.Rmd', eval = TRUE}
```

#### Diastolic Blood Pressure (Continuous)
```{r child = 'logistic/bp.diastolic.Rmd', eval = TRUE}
```

#### Diastolic Blood Pressure (Categorical)
```{r child = 'logistic/bp.diastolic.cat.Rmd', eval = TRUE}
```

#### Systolic Blood Pressure (Continuous)
```{r child = 'logistic/bp.systolic.Rmd', eval = TRUE}
```

#### Systolic Blood Pressure (Categorical)
```{r child = 'logistic/bp.systolic.cat.Rmd', eval = TRUE}
```

#### Heart Rate (Continuous)
```{r child = 'logistic/heart.rate.Rmd', eval = TRUE}
```

#### Heart Rate (Categorical)
```{r child = 'logistic/heart.rate.cat.Rmd', eval = TRUE}
```

#### Oxygen Saturation (Continuous)
```{r child = 'logistic/o2.saturation.Rmd', eval = TRUE}
```

#### Oxygen Saturation (Categorical)
```{r child = 'logistic/o2.saturation.cat.Rmd', eval = TRUE}
```

#### Respiratory Rate (Continuous)
```{r child = 'logistic/respiratory.rate.Rmd', eval = TRUE}
```

#### Respiratory Rate (Categorical)
```{r child = 'logistic/respiratory.rate.cat.Rmd', eval = TRUE}
```

#### History of IV Drug Use
```{r child = 'logistic/history.iv.drug.Rmd', eval = TRUE}
```

#### Family History of Thrombosis
```{r child = 'logistic/history.thrombosis.Rmd', eval = TRUE}
```

#### History of Varicose Veins
```{r child = 'logistic/history.veins.Rmd', eval = TRUE}
```

#### Previous Pregnancy Problems
```{r child = 'logistic/prev.preg.problem.Rmd', eval = TRUE}
```

#### Problems with Current Pregnancy
```{r child = 'logistic/this.pregnancy.problems.Rmd', eval = TRUE}
```

#### Multiple Pregnancy
```{r child = 'logistic/multiple.preg.Rmd', eval = TRUE}
```

#### Trimester
```{r child = 'logistic/trimester.Rmd', eval = TRUE}
```

#### One or more Pregnancy > 24 weeks
```{r child = 'logistic/pregnancies.over.Rmd', eval = TRUE}
```

#### Known Thrombophilia
```{r child = 'logistic/thrombo.Rmd', eval = TRUE}
```

#### History of Thrombosis
```{r child = 'logistic/thrombosis.Rmd', eval = TRUE}
```

#### History of Thromboprophylaxis
```{r child = 'logistic/thromboprophylaxis.Rmd', eval = TRUE}
```

#### Injury
```{r child = 'logistic/injury.Rmd', eval = TRUE}
```

#### Surgery
```{r child = 'logistic/surgery.Rmd', eval = TRUE}
```

#### Medical Complications (Delphi)
```{r child = 'logistic/medical.complication.Rmd', eval = FALSE}
```

#### Obstetric Complications (Delphi)
```{r child = 'logistic/obstetric.complication.Rmd', eval = FALSE}
```

#### Presenting Features - Pleuritic
```{r child = 'logistic/presenting.features.pleuritic.Rmd', eval = TRUE}
```

#### Presenting Features - Non-Pleuritic
```{r child = 'logistic/presenting.features.non.pleuritic.Rmd', eval = TRUE}
```

#### Presenting Features - Shortness of Breath (Exertion)
```{r child = 'logistic/presenting.features.sob.exertion.Rmd', eval = TRUE}
```

#### Presenting Features - Shortness of Breath (Rest)
```{r child = 'logistic/presenting.features.sob.rest.Rmd', eval = TRUE}
```

#### Presenting Features - Haemoptysis
```{r child = 'logistic/presenting.features.haemoptysis.Rmd', eval = TRUE}
```

#### Presenting Features - Cough
```{r child = 'logistic/presenting.features.cough.Rmd', eval = TRUE}
```

#### Presenting Features - Syncope
```{r child = 'logistic/presenting.features.syncope.Rmd', eval = TRUE}
```

#### Presenting Features - Palpitations
```{r child = 'logistic/presenting.features.palpitations.Rmd', eval = TRUE}
```

#### Presenting Features - Other
```{r child = 'logistic/presenting.features.other.Rmd', eval = TRUE}
```

#### X-Ray : PE Related
```{r child = 'logistic/xray.pe.Rmd', eval = TRUE}
```

#### ECG : PE Related
```{r child = 'logistic/ecg.pe.Rmd', eval = TRUE}
```

#### Geneva : Unilateral lower limb pain
```{r child = 'logistic/simplified.lower.limb.unilateral.pain.Rmd', eval = TRUE}
```

#### Geneva : Pain on Limb Palpitation
```{r child = 'logistic/simplified.lower.limb.unilateral.pain.Rmd', eval = TRUE}
```

#### Wells : PE most likely (Permissive)
```{r child = 'logistic/wells.alternative.permissive.Rmd', eval = TRUE}
```

#### Wells : PE most likely (Strict)
```{r child = 'logistic/wells.alternative.strict.Rmd', eval = TRUE}
```

#### PERC : Exogenous Estrogen
```{r child = 'logistic/perc.hormone.Rmd', eval = TRUE}
```

#### PERC : Unilateral Leg Swelling
```{r child = 'logistic/perc.leg.swelling.Rmd', eval = TRUE}
```

#### Delphi : Surgery (excl. Cesarean)
```{r child = 'logistic/delphi.medical.history.surgery.Rmd', eval = TRUE}
```

#### Delphi : Hospital Admission, Surgery (excl. Cesarean) or Injury
```{r child = 'logistic/delphi.medical.history.Rmd', eval = TRUE}
```

#### Delphi : Medical Complications
```{r child = 'logistic/delphi.medical.complication.Rmd', eval = TRUE}
```

#### Delphi : Obstetric Complications
```{r child = 'logistic/delphi.obstetric.complication.Rmd', eval = TRUE}
```

#### Delphi - Trimester
```{r child = 'logistic/delphi.gestation.Rmd', eval = TRUE}
```
