### Biomarkers {.tabset .tabset-fade .tabset-pills}


**NB** - Only the `Suspected PE` group had blood samples assayed for this work in a standardised laboratory setting.  The D-Dimer measurements for individuals identified as `Diagnosed PE` from the UKOSS cohort suffer from heterogeneity in laboratories and reagents.

The nomenclature for biomarkers used in the Statistical Analysis Plan were not used in the resulting data that was provided by [Kiran Parmar](mailto:kiran.parmar@kcl.ac.uk)

Table: Abbreviations used in supplied biomarker assays

| Biomarker                              | Abbreviations                   | Tab                                |
|:---------------------------------------|:--------------------------------|:-----------------------------------|
| Activated partial thromboplastin time  | APTT SP liquid                  | APTT |
| Clauss Fibrinogen                      | Clauss Fibrinogen               | Clauss Fibrinogen |
| Troponin I                             | Troponin I                      | Troponin |
| B-type Natriuretic Peptide             | NPPB                            | NPPB |
| MRProANP                               | MRProANP                        | MRProANP |
| Thrombin Generation                    | ttPeak                          | Thrombin Generation (Time to Peak) |
|                                        | Peak                            | Thrombin Generation (Peak) |
|                                        | ETP                             | Thrombin Generation (Endogenous Potential) |
|                                        | Lagtime                         | Thrombin Generation (Lag Time) |
| Plasmin Antiplasmin                    | PAP                             | Plasmin Antiplasmin |
| Soluble Tissue Factor                  | TF                              | Tissue Factor |
| D-Dimer latex aglutination (Innovance) | D-Dimer innovance latex test    | D-Dimer (Innovance) |
| D-Dimer (ELISA)                        | D-Dimer Eliza Zymutest (Hyphen) | D-Dimer (ELISA) |
| Prothrombin Time                       | PT                              | Prothrombin |
| Prothrombin Fragments 1 + 2            | PF 1 + 2                        | PF 1 + 2 |


```{r child = 'biomarkers/prep.Rmd', eval = TRUE}
```

#### All Assays {.tabset .tabset-fade .tabset-pills}

```{r child = 'biomarkers/results_all.Rmd', eval = TRUE}
```


#### Excluding those on Anti-Coagulants  {.tabset .tabset-fade .tabset-pills}

```{r child = 'biomarkers/results_excl_anti_coag.Rmd', eval = TRUE}
```

#### D-Dimer (Hospital)   {.tabset .tabset-fade .tabset-pills}

```{r child = 'biomarkers/ddimer.Rmd', eval = FALSE}
```







```{r child = 'biomarkers/biomarker_summary_all.Rmd', eval = FALSE}
```

```{r child = 'biomarkers/biomarker_logistic_all.Rmd', eval = FALSE}
```

```{r child = 'biomarkers/gestation_all.Rmd', eval = FALSE}
```

```{r child = 'biomarkers/biomarker_summary_excl_anti_coag.Rmd', eval = FALSE}
```

```{r child = 'biomarkers/biomarker_logistic_excl_anti_coag.Rmd', eval = FALSE}
```

```{r child = 'biomarkers/gestation_excl_anti_coag.Rmd', eval = FALSE}
```

```{r child = 'biomarkers/ddimer.Rmd', eval = FALSE}
```
