### Classification  {.tabset .tabset-fade .tabset-pills}

Case Reviews were performed by two independent reviewers using imaging, treatment and follow-up data blind to the physiological and patient questionnaire responses to classify individuals as either `PE`, `No PE` or `Exclude`.  If the reviews concurred then the classsification was accepted, if they did not a third independent review was performed and accepted as the classification.

Four classifications were derived and are summarised in the tables that follow.

| Imaging | Treatment | Follow-up | Primary | Secondary | Tertiary | Quaternary |
|:-------:|:---------:|:---------:|:--------|:----------|:---------|:-----------|
| `I1a`   | `T1`      | `F1`      | PE      | PE        | PE       | PE         |
| `I1a`   | `T1`      | `F2`      | PE      | PE        | PE       | PE         |
| `I1a`   | `T2`      | `F1`      | PE      | PE        | PE       | PE         |
| `I1a`   | `T2`      | `F2`      | PE      | PE        | PE       | PE         |
| `I1b`   | `T1`      | `F1`      | PE      | PE        | PE       | Exclude    |
| `I1b`   | `T1`      | `F2`      | PE      | PE        | PE       | Exclude    |
| `I1b`   | `T2`      | `F1`      | PE      | PE        | PE       | Exclude    |
| `I1b`   | `T2`      | `F2`      | PE      | PE        | PE       | Exclude    |
| `I2`    | `T1`      | `F1`      | PE      | PE        | PE       | PE         |
| `I2`    | `T1`      | `F2`      | Exclude | PE        | Exclude  | Exclude    |
| `I2`    | `T2`      | `F1`      | PE      | PE        | PE       | PE         |
| `I2`    | `T2`      | `F2`      | No PE   | No PE     | No PE    | No PE      |
| `I3`    | `T1`      | `F1`      | PE      | PE        | PE       | PE         |
| `I3`    | `T1`      | `F2`      | No PE   | No PE     | No PE    | No PE      |
| `I3`    | `T2`      | `F1`      | PE      | PE        | PE       | PE         |
| `I3`    | `T2`      | `F2`      | No PE   | No PE     | No PE    | No PE      |
| `I4`    | `T1`      | `F1`      | PE      | PE        | PE       | PE         |
| `I4`    | `T1`      | `F2`      | Exclude | PE        | Exclude  | Exclude    |
| `I4`    | `T2`      | `F1`      | PE      | PE        | PE       | PE         |
| `I4`    | `T2`      | `F2`      | Exclude | Exclude   | No PE    | Exclude    |

#### Reviewer 1

```{r results_classification_reviewer1, echo = FALSE, cache = FALSE, warning = FALSE, results = 'markup', eval = TRUE}
group_by(master$case.review, group, img.class1, trt.class1, fup.class1) %>%
    summarise(n = n()) %>%
    dplyr::filter(group != 'Diagnosed DVT') %>%
    dcast(img.class1 + trt.class1 + fup.class1 ~ group) %>%
    kable(col.names = c('Imaging', 'Treatment', 'Follow-Up', 'UKOSS', 'Non-Recruited', 'Suspected PE'),
          caption = 'Reviewer 1 Primary classification based on Image, Treatment and Follow-Up for data from three sources. **NB** Combinations that were NOT observed are NOT tabulated.')

```

#### Reviewer 2

```{r results_classification_reviewer2, echo = FALSE, cache = FALSE, warning = FALSE, results = 'markup', eval = TRUE}
group_by(master$case.review, group, img.class2, trt.class2, fup.class2) %>%
    summarise(n = n()) %>%
    dplyr::filter(group != 'Diagnosed DVT') %>%
    dcast(img.class2 + trt.class2 + fup.class2 ~ group) %>%
    kable(col.names = c('Imaging', 'Treatment', 'Follow-Up', 'UKOSS', 'Non-Recruited', 'Suspected PE'),
          caption = 'Reviewer 2 Primary classification based on Image, Treatment and Follow-Up for data from three sources. **NB** Combinations that were NOT observed are NOT tabulated.')

```

#### Reviewer 3

```{r results_classification_reviewer3, echo = FALSE, cache = FALSE, warning = FALSE, results = 'markup', eval = TRUE}
group_by(master$case.review, group, img.class3, trt.class3, fup.class3) %>%
    summarise(n = n()) %>%
    dplyr::filter(group != 'Diagnosed DVT') %>%
    dcast(img.class3 + trt.class3 + fup.class3 ~ group) %>%
    dplyr::filter(!is.na(img.class3)) %>%
    kable(col.names = c('Imaging', 'Treatment', 'Follow-Up', 'UKOSS', 'Non-Recruited', 'Suspected PE'),
          caption = 'Reviewer 3 Primary classification based on Image, Treatment and Follow-Up for data from three sources. **NB** Combinations that were NOT observed are NOT tabulated.')

```

#### Overall Classifications


```{r results_classification_overall, echo = FALSE, cache = FALSE, warning = FALSE, results = 'markup', eval = TRUE}

## Remove DVT
to.table <- dplyr::filter(dipep, group != 'Diagnosed DVT') %>%
            dplyr::select(group, first.st, second.st, third.st, fourth.st)
## Counts by each classification
## ToDo 20170220 - Should perhaps have this done using dplyr function to repeat over columns
##                 insufficient time to spend on working that out.
primary <- group_by(to.table, group, first.st) %>%
    summarise(n = n())
names(primary) <- gsub('first.st', 'class', names(primary))
primary$classification <- 'Primary'
secondary <- group_by(to.table, group, second.st) %>%
    summarise(n = n())
names(secondary) <- gsub('second.st', 'class', names(secondary))
secondary$classification <- 'Secondary'
tertiary <- group_by(to.table, group, third.st) %>%
            summarise(n = n())
names(tertiary) <- gsub('third.st', 'class', names(tertiary))
tertiary$classification <- 'Tertiary'
quaternary <- group_by(to.table, group, fourth.st) %>%
            summarise(n = n())
names(quaternary) <- gsub('fourth.st', 'class', names(quaternary))
quaternary$classification <- 'Quaternary'
to.table <- rbind(primary,
                  secondary,
                  tertiary,
                  quaternary) %>%
            dcast(classification ~ group + class, value.var = 'n')
names(to.table) <- gsub('classification', 'Classification', names(to.table))
names(to.table) <- gsub('Diagnosed PE', 'UKOSS', names(to.table))
names(to.table) <- gsub('_PE', ' (PE)', names(to.table))
names(to.table) <- gsub('_NA', ' (Missing)', names(to.table))
names(to.table) <- gsub('_No PE', ' (No PE)', names(to.table))
to.table <- to.table %>%
            mutate(order = case_when(.$Classification == 'Primary' ~ 1,
                                     .$Classification == 'Secondary' ~ 2,
                                     .$Classification == 'Tertiary' ~ 3,
                                     .$Classification == 'Quaternary' ~ 4)) %>%
            arrange(order) %>%
            dplyr::select(-c(order))
kable(to.table,
      caption = 'Overall classifications for UKOSS, Suspected PE and Non-recruited individuals for the four different classification rules (see above table).')
rm(to.table)

```
