### Demographics {.tabset .tabset-fade .tabset-pills}

```{r demograhpics_summary, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
## Derive summary numbers for use in text
n_ethnicity          <- unique(dipep$ethnicity) %>% length()
nonmissing_ethnicity <- filter(dipep, !is.na(ethnicity)) %>% nrow()
missing_ethnicity    <- filter(dipep, is.na(ethnicity)) %>% nrow()
## ## TODO - Replace with extracting values from summary data frames
## BMI
## bmi_summary <- dipep_summarise(df     = dipep,
##                                to.sum = bmi)
bmi_mean    <- mean(dipep$bmi, na.rm = TRUE)
bmi_sd      <- sd(dipep$bmi, na.rm = TRUE)
bmi_median  <- quantile(dipep$bmi, probs = 0.5, na.rm = TRUE)
bmi_p25     <- quantile(dipep$bmi, probs = 0.25, na.rm = TRUE)
bmi_p75     <- quantile(dipep$bmi, probs = 0.75, na.rm = TRUE)
bmi_min     <- min(dipep$bmi, na.rm = TRUE)
bmi_max     <- max(dipep$bmi, na.rm = TRUE)
bmi_missing <- filter(dipep, is.na(bmi)) %>% nrow()
## BMI - Suspected PE
bmi_suspected_pe_mean    <- filter(dipep, group == 'Suspected PE') %>% mean(bmi, na.rm = TRUE)
## bmi_suspected_pe_sd      <- filter(dipep, group == 'Suspected PE') %>% sd(bmi, na.rm = TRUE)
## bmi_suspected_pe_median  <- filter(dipep, group == 'Suspected PE') %>% quantile(bmi, probs = 0.5, na.rm = TRUE)
## bmi_suspected_pe_p25     <- filter(dipep, group == 'Suspected PE') %>% quantile(bmi, probs = 0.25, na.rm = TRUE)
## bmi_suspected_pe_p75     <- filter(dipep, group == 'Suspected PE') %>% quantile(bmi, probs = 0.75, na.rm = TRUE)
## bmi_suspected_pe_min     <- filter(dipep, group == 'Suspected PE') %>% min(bmi, na.rm = TRUE)
## bmi_suspected_pe_max     <- filter(dipep, group == 'Suspected PE') %>% min(bmi, na.rm = TRUE)
## bmi_suspected_pe_missing <- filter(dipep, group == 'Suspected PE' & is.na(bmi)) %>% nrow()
## Age
## age_summary <- dipep_summarise(df     = dipep,
##                                to.sum = age)
age_mean    <- mean(dipep$age, na.rm = TRUE)
age_sd      <- sd(dipep$age, na.rm = TRUE)
age_median  <- quantile(dipep$age, probs = 0.5, na.rm = TRUE)
age_p25     <- quantile(dipep$age, probs = 0.25, na.rm = TRUE)
age_p75     <- quantile(dipep$age, probs = 0.75, na.rm = TRUE)
age_min     <- min(dipep$age, na.rm = TRUE)
age_max     <- max(dipep$age, na.rm = TRUE)
age_missing <- filter(dipep, is.na(age)) %>% nrow()
## Age - Suspected PE
age_suspected_pe_mean    <- filter(dipep, group == 'Suspected PE') %>% mean(age, na.rm = TRUE)
## age_suspected_pe_sd      <- filter(dipep, group == 'Suspected PE') %>% sd(age, na.rm = TRUE)
## age_suspected_pe_median  <- filter(dipep, group == 'Suspected PE') %>% quantile(age, probs = 0.5, na.rm = TRUE)
## age_suspected_pe_p25     <- filter(dipep, group == 'Suspected PE') %>% quantile(age, probs = 0.25, na.rm = TRUE)
## age_suspected_pe_p75     <- filter(dipep, group == 'Suspected PE') %>% quantile(age, probs = 0.75, na.rm = TRUE)
## age_suspected_pe_min     <- filter(dipep, group == 'Suspected PE') %>% min(age, na.rm = TRUE)
## age_suspected_pe_max     <- filter(dipep, group == 'Suspected PE') %>% min(age, na.rm = TRUE)
## age_suspected_pe_missing <- filter(dipep, group == 'Suspected PE' & is.na(age)) %>% nrow()

## Height
## height_summary <- dipep_summarise(df     = dipep,
##                                to.sum = height)
height_mean    <- mean(dipep$height, na.rm = TRUE)
height_sd      <- sd(dipep$height, na.rm = TRUE)
height_median  <- quantile(dipep$height, probs = 0.5, na.rm = TRUE)
height_p25     <- quantile(dipep$height, probs = 0.25, na.rm = TRUE)
height_p75     <- quantile(dipep$height, probs = 0.75, na.rm = TRUE)
height_min     <- min(dipep$height, na.rm = TRUE)
height_max     <- max(dipep$height, na.rm = TRUE)
height_missing <- filter(dipep, is.na(height)) %>% nrow()
## Height - Suspected PE
height_suspected_pe_mean    <- filter(dipep, group == 'Suspected PE') %>% mean(height, na.rm = TRUE)
## height_suspected_pe_sd      <- filter(dipep, group == 'Suspected PE') %>% sd(height, na.rm = TRUE)
## height_suspected_pe_median  <- filter(dipep, group == 'Suspected PE') %>% quantile(height, probs = 0.5, na.rm = TRUE)
## height_suspected_pe_p25     <- filter(dipep, group == 'Suspected PE') %>% quantile(height, probs = 0.25, na.rm = TRUE)
## height_suspected_pe_p75     <- filter(dipep, group == 'Suspected PE') %>% quantile(height, probs = 0.75, na.rm = TRUE)
## height_suspected_pe_min     <- filter(dipep, group == 'Suspected PE') %>% min(height, na.rm = TRUE)
## height_suspected_pe_max     <- filter(dipep, group == 'Suspected PE') %>% min(height, na.rm = TRUE)
## height_suspected_pe_missing <- filter(dipep, group == 'Suspected PE' & is.na(height)) %>% nrow()

## Weight
## weight_summary <- dipep_summarise(df     = dipep,
##                                to.sum = weight)
weight_mean    <- mean(dipep$weight, na.rm = TRUE)
weight_sd      <- sd(dipep$weight, na.rm = TRUE)
weight_median  <- quantile(dipep$weight, probs = 0.5, na.rm = TRUE)
weight_p25     <- quantile(dipep$weight, probs = 0.25, na.rm = TRUE)
weight_p75     <- quantile(dipep$weight, probs = 0.75, na.rm = TRUE)
weight_min     <- min(dipep$weight, na.rm = TRUE)
weight_max     <- max(dipep$weight, na.rm = TRUE)
weight_missing <- filter(dipep, is.na(weight)) %>% nrow()
## Weight - Suspected PE
weight_suspected_pe_mean    <- filter(dipep, group == 'Suspected PE') %>% mean(weight, na.rm = TRUE)
## weight_suspected_pe_sd      <- filter(dipep, group == 'Suspected PE') %>% sd(weight, na.rm = TRUE)
## weight_suspected_pe_median  <- filter(dipep, group == 'Suspected PE') %>% quantile(weight, probs = 0.5, na.rm = TRUE)
## weight_suspected_pe_p25     <- filter(dipep, group == 'Suspected PE') %>% quantile(weight, probs = 0.25, na.rm = TRUE)
## weight_suspected_pe_p75     <- filter(dipep, group == 'Suspected PE') %>% quantile(weight, probs = 0.75, na.rm = TRUE)
## weight_suspected_pe_min     <- filter(dipep, group == 'Suspected PE') %>% min(weight, na.rm = TRUE)
## weight_suspected_pe_max     <- filter(dipep, group == 'Suspected PE') %>% min(weight, na.rm = TRUE)
## weight_suspected_pe_missing <- filter(dipep, group == 'Suspected PE' & is.na(weight)) %>% nrow()

## Heart Rate
## heart_rate_summary <- dipep_summarise(df     = dipep,
##                                to.sum = heart.rate)
heart_rate_mean    <- mean(dipep$heart.rate, na.rm = TRUE)
heart_rate_sd      <- sd(dipep$heart.rate, na.rm = TRUE)
heart_rate_median  <- quantile(dipep$heart.rate, probs = 0.5, na.rm = TRUE)
heart_rate_p25     <- quantile(dipep$heart.rate, probs = 0.25, na.rm = TRUE)
heart_rate_p75     <- quantile(dipep$heart.rate, probs = 0.75, na.rm = TRUE)
heart_rate_min     <- min(dipep$heart.rate, na.rm = TRUE)
heart_rate_max     <- max(dipep$heart.rate, na.rm = TRUE)
heart_rate_missing <- filter(dipep, is.na(heart.rate)) %>% nrow()
## Heart Rate - Suspected PE
heart_rate_suspected_pe_mean    <- filter(dipep, group == 'Suspected PE') %>% mean(heart.rate, na.rm = TRUE)
## heart_rate_suspected_pe_sd      <- filter(dipep, group == 'Suspected PE') %>% sd(heart.rate, na.rm = TRUE)
## heart_rate_suspected_pe_median  <- filter(dipep, group == 'Suspected PE') %>% quantile(heart.rate, probs = 0.5, na.rm = TRUE)
## heart_rate_suspected_pe_p25     <- filter(dipep, group == 'Suspected PE') %>% quantile(heart.rate, probs = 0.25, na.rm = TRUE)
## heart_rate_suspected_pe_p75     <- filter(dipep, group == 'Suspected PE') %>% quantile(heart.rate, probs = 0.75, na.rm = TRUE)
## heart_rate_suspected_pe_min     <- filter(dipep, group == 'Suspected PE') %>% min(heart.rate, na.rm = TRUE)
## heart_rate_suspected_pe_max     <- filter(dipep, group == 'Suspected PE') %>% min(heart.rate, na.rm = TRUE)
## heart_rate_suspected_pe_missing <- filter(dipep, group == 'Suspected PE' & is.na(heart.rate)) %>% nrow()

## Respiratory Rate
## respiratory_rate_summary <- dipep_summarise(df     = dipep,
##                                to.sum = respiratory.rate)
respiratory_rate_mean    <- mean(dipep$respiratory.rate, na.rm = TRUE)
respiratory_rate_sd      <- sd(dipep$respiratory.rate, na.rm = TRUE)
respiratory_rate_median  <- quantile(dipep$respiratory.rate, probs = 0.5, na.rm = TRUE)
respiratory_rate_p25     <- quantile(dipep$respiratory.rate, probs = 0.25, na.rm = TRUE)
respiratory_rate_p75     <- quantile(dipep$respiratory.rate, probs = 0.75, na.rm = TRUE)
respiratory_rate_min     <- min(dipep$respiratory.rate, na.rm = TRUE)
respiratory_rate_max     <- max(dipep$respiratory.rate, na.rm = TRUE)
respiratory_rate_missing <- filter(dipep, is.na(respiratory.rate)) %>% nrow()
## Respiratory Rate - Suspected PE
respiratory_rate_suspected_pe_mean    <- filter(dipep, group == 'Suspected PE') %>% mean(respiratory.rate, na.rm = TRUE)
## respiratory_rate_suspected_pe_sd      <- filter(dipep, group == 'Suspected PE') %>% sd(respiratory.rate, na.rm = TRUE)
## respiratory_rate_suspected_pe_median  <- filter(dipep, group == 'Suspected PE') %>% quantile(respiratory.rate, probs = 0.5, na.rm = TRUE)
## respiratory_rate_suspected_pe_p25     <- filter(dipep, group == 'Suspected PE') %>% quantile(respiratory.rate, probs = 0.25, na.rm = TRUE)
## respiratory_rate_suspected_pe_p75     <- filter(dipep, group == 'Suspected PE') %>% quantile(respiratory.rate, probs = 0.75, na.rm = TRUE)
## respiratory_rate_suspected_pe_min     <- filter(dipep, group == 'Suspected PE') %>% min(respiratory.rate, na.rm = TRUE)
## respiratory_rate_suspected_pe_max     <- filter(dipep, group == 'Suspected PE') %>% min(respiratory.rate, na.rm = TRUE)
## respiratory_rate_suspected_pe_missing <- filter(dipep, group == 'Suspected PE' & is.na(respiratory.rate)) %>% nrow()

## Systolic BP
## systolic_summary <- dipep_summarise(df     = dipep,
##                                to.sum = bp.systolic)
systolic_mean    <- mean(dipep$bp.systolic, na.rm = TRUE)
systolic_sd      <- sd(dipep$bp.systolic, na.rm = TRUE)
systolic_median  <- quantile(dipep$bp.systolic, probs = 0.5, na.rm = TRUE)
systolic_p25     <- quantile(dipep$bp.systolic, probs = 0.25, na.rm = TRUE)
systolic_p75     <- quantile(dipep$bp.systolic, probs = 0.75, na.rm = TRUE)
systolic_min     <- min(dipep$bp.systolic, na.rm = TRUE)
systolic_max     <- max(dipep$bp.systolic, na.rm = TRUE)
systolic_missing <- filter(dipep, is.na(bp.systolic)) %>% nrow()
## Systolic BP - Suspected PE
systolic_suspected_pe_mean    <- filter(dipep, group == 'Suspected PE') %>% mean(bp.systolic, na.rm = TRUE)
## systolic_suspected_pe_sd      <- filter(dipep, group == 'Suspected PE') %>% sd(bp.systolic, na.rm = TRUE)
## systolic_suspected_pe_median  <- filter(dipep, group == 'Suspected PE') %>% quantile(bp.systolic, probs = 0.5, na.rm = TRUE)
## systolic_suspected_pe_p25     <- filter(dipep, group == 'Suspected PE') %>% quantile(bp.systolic, probs = 0.25, na.rm = TRUE)
## systolic_suspected_pe_p75     <- filter(dipep, group == 'Suspected PE') %>% quantile(bp.systolic, probs = 0.75, na.rm = TRUE)
## systolic_suspected_pe_min     <- filter(dipep, group == 'Suspected PE') %>% min(bp.systolic, na.rm = TRUE)
## systolic_suspected_pe_max     <- filter(dipep, group == 'Suspected PE') %>% min(bp.systolic, na.rm = TRUE)
## systolic_suspected_pe_missing <- filter(dipep, group == 'Suspected PE' & is.na(bp.systolic)) %>% nrow()

## Diastolic BP
## diastolic_summary <- dipep_summarise(df     = dipep,
##                                to.sum = bp.diastolic)
diastolic_mean    <- mean(dipep$bp.diastolic, na.rm = TRUE)
diastolic_sd      <- sd(dipep$bp.diastolic, na.rm = TRUE)
diastolic_median  <- quantile(dipep$bp.diastolic, probs = 0.5, na.rm = TRUE)
diastolic_p25     <- quantile(dipep$bp.diastolic, probs = 0.25, na.rm = TRUE)
diastolic_p75     <- quantile(dipep$bp.diastolic, probs = 0.75, na.rm = TRUE)
diastolic_min     <- min(dipep$bp.diastolic, na.rm = TRUE)
diastolic_max     <- max(dipep$bp.diastolic, na.rm = TRUE)
diastolic_missing <- filter(dipep, is.na(bp.diastolic)) %>% nrow()
## Diastolic BP - Suspected PE
diastolic_suspected_pe_mean    <- filter(dipep, group == 'Suspected PE') %>% mean(bp.diastolic, na.rm = TRUE)
## diastolic_suspected_pe_sd      <- filter(dipep, group == 'Suspected PE') %>% sd(bp.diastolic, na.rm = TRUE)
## diastolic_suspected_pe_median  <- filter(dipep, group == 'Suspected PE') %>% quantile(bp.diastolic, probs = 0.5, na.rm = TRUE)
## diastolic_suspected_pe_p25     <- filter(dipep, group == 'Suspected PE') %>% quantile(bp.diastolic, probs = 0.25, na.rm = TRUE)
## diastolic_suspected_pe_p75     <- filter(dipep, group == 'Suspected PE') %>% quantile(bp.diastolic, probs = 0.75, na.rm = TRUE)
## diastolic_suspected_pe_min     <- filter(dipep, group == 'Suspected PE') %>% min(bp.diastolic, na.rm = TRUE)
## diastolic_suspected_pe_max     <- filter(dipep, group == 'Suspected PE') %>% min(bp.diastolic, na.rm = TRUE)
## diastolic_suspected_pe_missing <- filter(dipep, group == 'Suspected PE' & is.na(bp.diastolic)) %>% nrow()

## Summary by group
summary.stats <- list()
summary.stats$group       <-  dipep_summarise(df                    = dipep,
                                              grouping              = 'group',
                                              group.as.col          = TRUE,
                                              exclude               = NULL,
                                              exclude.non.recruited = FALSE,
                                              exclude.dvt           = FALSE,
                                              age, bmi, heart.rate, bp.systolic, bp.diastolic, height,
                                              weight, respiratory.rate, o2.saturation, gestation)
summary.stats$first.st <- dipep_summarise(df           = dipep,
                      	                  grouping     = 'first.st',
                      	                  group.as.col = TRUE,
                                          exclude               = NULL,
                                          exclude.non.recruited = TRUE,
                                          exclude.dvt           = TRUE,
                      	                  age, bmi, heart.rate, bp.systolic, bp.diastolic, height,
                      	                  weight, respiratory.rate, o2.saturation, gestation)
summary.stats$second.st <- dipep_summarise(df           = dipep,
                                           grouping     = 'second.st',
                                           group.as.col = TRUE,
                                           exclude               = NULL,
                                           exclude.non.recruited = TRUE,
                                           exclude.dvt           = TRUE,
                                           age, bmi, heart.rate, bp.systolic, bp.diastolic, height,
                                           weight, respiratory.rate, o2.saturation, gestation)
summary.stats$third.st <- dipep_summarise(df           = dipep,
                   	    	          grouping     = 'third.st',
                       	                  group.as.col = TRUE,
                                          exclude               = NULL,
                                          exclude.non.recruited = TRUE,
                                          exclude.dvt           = TRUE,
                       	                  age, bmi, heart.rate, bp.systolic, bp.diastolic, height,
                       	                  weight, respiratory.rate, o2.saturation, gestation)
summary.stats$fourth.st <- dipep_summarise(df           = dipep,
                    	    	           grouping     = 'fourth.st',
                       	                   group.as.col = TRUE,
                                           exclude               = NULL,
                                           exclude.non.recruited = TRUE,
                                           exclude.dvt           = TRUE,
                       	                   age, bmi, heart.rate, bp.systolic, bp.diastolic, height,
                       	                   weight, respiratory.rate, o2.saturation, gestation)

```

#### Ethnicity

Of the `r n_screened` individuals screened `r n_ethnicity` unique ethnicities were recorded for `r nonmissing_ethnicity` individuals and was missing for `r missing_ethnicity` individuals.  Table  details the frequency of recorded ethnicities and these are plotted in figure

```{r  demographics_table_ethnicity, echo = FALSE, cache = FALSE, results = 'markup', eval = FALSE}
kable(ethnicity, group)
```

```{r  demographics_figure_ethnicity, echo = FALSE, cache = FALSE, results = 'hide', fig.width = 10, eval = TRUE}
dplyr::select(dipep, ethnicity, group) %>%
    ggplot(aes(x    = ethnicity,
               fill = ethnicity)) +
    geom_bar() +
    xlab('') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~group, ncol = 3) + theme_bw() +
    theme(axis.text.x = element_text(angle = 90))

```


#### Age

The overall mean age in years of those was `r age_mean` (SD `r age_sd`; Median `r age_median` (IQR `r age_p25` to `r age_p75`); Range `r age_min` to `r age_max`) and the distribution of ages by group is summarised in figure and table below.

```{r  demographics_figure_age_group, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df                    = dipep,
                      exclude               = NULL,
                      exclude.non.recruited = FALSE,
                      exclude.dvt           = FALSE,
                      title.to.plot         = 'Age (Years)',
                      title.class           = 'Recruitment',
                      group, age)
to.plot$histogram
## to.plot$scatter
dplyr::filter(summary.stats$group, Measurement == 'Age') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Age by Recruitment Group')
```

```{r  demographics_figure_age_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df                    = dipep,
                      exclude               = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot         = 'Age (Years)',
                      title.class           = 'Primary Classification',
                      first.st, age)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.stats$first.st, Measurement == 'Age') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Age by Primary Classification')


```

#### BMI

The overall mean BMI was `r bmi_mean` (SD `r bmi_sd`; Median `r bmi_median` (IQR `r bmi_p25` to `r bmi_p75`); Range `r bmi_min` to `r bmi_max`) and the distribution of BMI by group is summarised in figure and table below.


```{r  demographics_figure_bmi_group, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df                    = dipep,
                      exclude               = NULL,
                      exclude.non.recruited = FALSE,
                      exclude.dvt           = FALSE,
                      title.to.plot         = 'BMI',
                      title.class           = 'Recruitment',
                      group, bmi)
to.plot$histogram
## to.plot$scatter
dplyr::filter(summary.stats$group, Measurement == 'BMI') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of BMI by Recruitment Group')


```

```{r  demographics_figure_bmi_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df                    = dipep,
                      exclude               = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot         = 'BMI',
                      title.class           = 'Primary Classification',
                      first.st, bmi)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.stats$first.st, Measurement == 'BMI') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of BMI by Primary Classification')


```

#### Height

The overall mean height in centimetres (cm) was `r height_mean` (SD `r height_sd`; Median `r height_median` (IQR `r height_p25` to `r height_p75`); Range `r height_min` to `r height_max`) and the distribution of heights by group is summarised in figure and table below.


```{r  demographics_figure_height_group, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df                    = dipep,
                      exclude               = NULL,
                      exclude.non.recruited = FALSE,
                      exclude.dvt           = FALSE,
                      title.to.plot         = 'Height (cm)',
                      title.class           = 'Recruitment',
                      group, height)
to.plot$histogram
## to.plot$scatter
dplyr::filter(summary.stats$group, Measurement == 'Height') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Height by Recruitment Group')

```

```{r  demographics_figure_height_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df                    = dipep,
                      exclude               = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot         = 'Height (cm)',
                      title.class           = 'Primary Classification',
                      first.st, height)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.stats$first.st, Measurement == 'Height') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Height by Primary Classification')

```

#### Weight

The mean weight in kilgrams (kg) was `r weight_mean` (SD `r weight_sd`; Median `r weight_median` (IQR `r weight_p25` to `r weight_p75`); Range `r weight_min` to `r weight_max`) and the distribution of weights by group is summarised in figure and table below.


```{r  demographics_figure_weight_group, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df                    = dipep,
                      exclude               = NULL,
                      exclude.non.recruited = FALSE,
                      exclude.dvt           = FALSE,
                      title.to.plot         = 'Weight (kg)',
                      title.class           = 'Recruitment',
                      group, weight)
to.plot$histogram
## to.plot$scatter
dplyr::filter(summary.stats$group, Measurement == 'Weight') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Weight by Recruitment Group')

```

```{r  demographics_figure_weight_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df                    = dipep,
                      exclude               = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot         = 'Weight (kg)',
                      title.class           = 'Primary Classification',
                      first.st, weight)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.stats$first.st, Measurement == 'Weight') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Weight by Primary Classification')

```

#### Heart Rate

The overall mean heart rate in beats per minute (BPM) was `r heart_rate_mean` (SD `r heart_rate_sd`; Median `r heart_rate_median` (IQR `r heart_rate_p25` to `r heart_rate_p75`); Range `r heart_rate_min` to `r heart_rate_max`) and the distribution of weights by group is summarised in figure and table below.


```{r  demographics_figure_heart_rate_group, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df                    = dipep,
                      exclude               = NULL,
                      exclude.non.recruited = FALSE,
                      exclude.dvt           = FALSE,
                      title.to.plot         = 'Heart Rate (bpm)',
                      title.class           = 'Recruitment',
                      group, heart.rate)
to.plot$histogram
## to.plot$scatter
dplyr::filter(summary.stats$group, Measurement == 'Heart Rate') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Heart Rate by Recruitment Group')

```

```{r  demographics_figure_heart_rate_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df                    = dipep,
                      exclude               = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot         = 'Heart Rate (bpm)',
                      title.class           = 'Primary Classification',
                      first.st, heart.rate)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.stats$first.st, Measurement == 'Heart Rate') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Heart Rate by Primary Classification')

```


#### Respiratory Rate

The overall mean respiratory rate in breaths per minute (BPM) was `r respiratory_rate_mean` (SD `r respiratory_rate_sd`; Median `r respiratory_rate_median` (IQR `r respiratory_rate_p25` to `r respiratory_rate_p75`); Range `r respiratory_rate_min` to `r respiratory_rate_max`) and the distribution of weights by group is summarised in figure and table below.


```{r  demographics_figure_respiratory_rate_group, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df                    = dipep,
                      exclude               = NULL,
                      exclude.non.recruited = FALSE,
                      exclude.dvt           = FALSE,
                      title.to.plot         = 'Respiratory Rate (bpm)',
                      title.class           = 'Recruitment',
                      group, respiratory.rate)
to.plot$histogram
## to.plot$scatter
dplyr::filter(summary.stats$group, Measurement == 'Respiratory Rate') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Respiratory Rate (BPM) by Recruitment Group')

```

```{r  demographics_figure_respiratory_rate_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df                    = dipep,
                      exclude               = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot         = 'Respiratory Rate (bpm)',
                      title.class           = 'Primary Classification',
                      first.st, respiratory.rate)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.stats$first.st, Measurement == 'Respiratory Rate') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Respiratory Rate (BPM) by Primary Classification')

```

#### Systolic Blood Pressure

The overall mean systolic blood pressure in millimetres of mercury (mmHg) was `r systolic_mean` (SD `r systolic_sd`; Median `r systolic_median` (IQR `r systolic_p25` to `r systolic_p75`); Range `r systolic_min` to `r systolic_max`) and the distribution of weights by group is summarised in figure and table below.


```{r  demographics_figure_systolic_group, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df                    = dipep,
                      exclude               = NULL,
                      exclude.non.recruited = FALSE,
                      exclude.dvt           = FALSE,
                      title.to.plot         = 'Systolic BP (mmHg)',
                      title.class           = 'Recruitment',
                      group, bp.systolic)
to.plot$histogram
## to.plot$scatter
dplyr::filter(summary.stats$group, Measurement == 'Systolic BP') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Systolic Blood Pressure (mm/Hg) by Recruitment Group')

```

```{r  demographics_figure_systolic_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df                    = dipep,
                      exclude               = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot         = 'Systolic BP (mmHg)',
                      title.class           = 'Primary Classification',
                      first.st, bp.systolic)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.stats$first.st, Measurement == 'Systolic BP') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Systolic Blood Pressure (mm/Hg) by Primary Classification')

```

#### Diastolic Blood Pressure

The overall mean diastolic blood pressure in millimetres of mercury (mmHg) was `r diastolic_mean` (SD `r diastolic_sd`; Median `r diastolic_median` (IQR `r diastolic_p25` to `r diastolic_p75`); Range `r diastolic_min` to `r diastolic_max`) and the distribution of weights by group is summarised in figure and table below.


```{r  demographics_figure_diastolic_group, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df                    = dipep,
                      exclude               = NULL,
                      exclude.non.recruited = FALSE,
                      exclude.dvt           = FALSE,
                      title.to.plot         = 'Diastolic BP (mmHg)',
                      title.class           = 'Recruitment',
                      group, bp.diastolic)
to.plot$histogram
## to.plot$scatter
dplyr::filter(summary.stats$group, Measurement == 'Diastolic BP') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Diastolic Blood Pressure (mmHg) by Recruitment Group')

```

```{r  demographics_figure_diastolic_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df                    = dipep,
                      exclude               = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot         = 'Diastolic BP (mmHg)',
                      title.class           = 'Primary Classification',
                      first.st, bp.diastolic)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.stats$first.st, Measurement == 'Diastolic BP') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Diastolic Blood Pressure (mm/Hg) by Primary Classification')

```

#### Oxygen Saturation

The overall mean oxygen saturation as a percentage (%) was `r diastolic_mean` (SD `r diastolic_sd`; Median `r diastolic_median` (IQR `r diastolic_p25` to `r diastolic_p75`); Range `r diastolic_min` to `r diastolic_max`) and the distribution of weights by group is summarised in figure and table below.


```{r  demographics_figure_o2_saturation_group, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df                    = dipep,
                      exclude               = NULL,
                      exclude.non.recruited = FALSE,
                      exclude.dvt           = FALSE,
                      title.to.plot         = 'Oxygen Saturation (%)',
                      title.class           = 'Recruitment',
                      group, o2.saturation)
to.plot$histogram
## to.plot$scatter
dplyr::filter(summary.stats$group, Measurement == 'Oxygen Saturation') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Oxygen Saturation by Recruitment Group')

```

```{r  demographics_figure_o2_saturation_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
to.plot <- dipep_plot(df                    = dipep,
                      exclude               = NULL,
                      exclude.non.recruited = TRUE,
                      exclude.dvt           = TRUE,
                      title.to.plot         = 'Oxygen Saturation (%)',
                      title.class           = 'Primary Classification',
                      first.st, o2.saturation)
to.plot$histogram
to.plot$scatter
dplyr::filter(summary.stats$first.st, Measurement == 'Oxygen Saturation') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Oxygen Saturation by Primary Classification')

```
