### Demographics {.tabset .tabset-fade .tabset-pills}

```{r demograhpics_summary, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
## Derive summary numbers for use in text
n_ethnicity          <- unique(dipep$ethnicity) %>% length()
nonmissing_ethnicity <- filter(dipep, !is.na(ethnicity)) %>% nrow()
missing_ethnicity    <- filter(dipep, is.na(ethnicity)) %>% nrow()
## ## TODO - Replace with extracting values from summary data frames
## BMI
## bmi_summary <- dipep_summarise(df     = dipep,
##                                to.sum = bmi)
bmi_mean    <- mean(dipep$bmi, na.rm = TRUE)
bmi_sd      <- sd(dipep$bmi, na.rm = TRUE)
bmi_median  <- quantile(dipep$bmi, probs = 0.5, na.rm = TRUE)
bmi_p25     <- quantile(dipep$bmi, probs = 0.25, na.rm = TRUE)
bmi_p75     <- quantile(dipep$bmi, probs = 0.75, na.rm = TRUE)
bmi_min     <- min(dipep$bmi, na.rm = TRUE)
bmi_max     <- max(dipep$bmi, na.rm = TRUE)
bmi_missing <- filter(dipep, is.na(bmi)) %>% nrow()
## BMI - Suspected PE
bmi_suspected_pe_mean    <- filter(dipep, group == 'Suspected PE') %>% mean(bmi, na.rm = TRUE)
## bmi_suspected_pe_sd      <- filter(dipep, group == 'Suspected PE') %>% sd(bmi, na.rm = TRUE)
## bmi_suspected_pe_median  <- filter(dipep, group == 'Suspected PE') %>% quantile(bmi, probs = 0.5, na.rm = TRUE)
## bmi_suspected_pe_p25     <- filter(dipep, group == 'Suspected PE') %>% quantile(bmi, probs = 0.25, na.rm = TRUE)
## bmi_suspected_pe_p75     <- filter(dipep, group == 'Suspected PE') %>% quantile(bmi, probs = 0.75, na.rm = TRUE)
## bmi_suspected_pe_min     <- filter(dipep, group == 'Suspected PE') %>% min(bmi, na.rm = TRUE)
## bmi_suspected_pe_max     <- filter(dipep, group == 'Suspected PE') %>% min(bmi, na.rm = TRUE)
## bmi_suspected_pe_missing <- filter(dipep, group == 'Suspected PE' & is.na(bmi)) %>% nrow()
## Age
## age_summary <- dipep_summarise(df     = dipep,
##                                to.sum = age)
age_mean    <- mean(dipep$age, na.rm = TRUE)
age_sd      <- sd(dipep$age, na.rm = TRUE)
age_median  <- quantile(dipep$age, probs = 0.5, na.rm = TRUE)
age_p25     <- quantile(dipep$age, probs = 0.25, na.rm = TRUE)
age_p75     <- quantile(dipep$age, probs = 0.75, na.rm = TRUE)
age_min     <- min(dipep$age, na.rm = TRUE)
age_max     <- max(dipep$age, na.rm = TRUE)
age_missing <- filter(dipep, is.na(age)) %>% nrow()
## Age - Suspected PE
age_suspected_pe_mean    <- filter(dipep, group == 'Suspected PE') %>% mean(age, na.rm = TRUE)
## age_suspected_pe_sd      <- filter(dipep, group == 'Suspected PE') %>% sd(age, na.rm = TRUE)
## age_suspected_pe_median  <- filter(dipep, group == 'Suspected PE') %>% quantile(age, probs = 0.5, na.rm = TRUE)
## age_suspected_pe_p25     <- filter(dipep, group == 'Suspected PE') %>% quantile(age, probs = 0.25, na.rm = TRUE)
## age_suspected_pe_p75     <- filter(dipep, group == 'Suspected PE') %>% quantile(age, probs = 0.75, na.rm = TRUE)
## age_suspected_pe_min     <- filter(dipep, group == 'Suspected PE') %>% min(age, na.rm = TRUE)
## age_suspected_pe_max     <- filter(dipep, group == 'Suspected PE') %>% min(age, na.rm = TRUE)
## age_suspected_pe_missing <- filter(dipep, group == 'Suspected PE' & is.na(age)) %>% nrow()

## Height
## height_summary <- dipep_summarise(df     = dipep,
##                                to.sum = height)
height_mean    <- mean(dipep$height, na.rm = TRUE)
height_sd      <- sd(dipep$height, na.rm = TRUE)
height_median  <- quantile(dipep$height, probs = 0.5, na.rm = TRUE)
height_p25     <- quantile(dipep$height, probs = 0.25, na.rm = TRUE)
height_p75     <- quantile(dipep$height, probs = 0.75, na.rm = TRUE)
height_min     <- min(dipep$height, na.rm = TRUE)
height_max     <- max(dipep$height, na.rm = TRUE)
height_missing <- filter(dipep, is.na(height)) %>% nrow()
## Height - Suspected PE
height_suspected_pe_mean    <- filter(dipep, group == 'Suspected PE') %>% mean(height, na.rm = TRUE)
## height_suspected_pe_sd      <- filter(dipep, group == 'Suspected PE') %>% sd(height, na.rm = TRUE)
## height_suspected_pe_median  <- filter(dipep, group == 'Suspected PE') %>% quantile(height, probs = 0.5, na.rm = TRUE)
## height_suspected_pe_p25     <- filter(dipep, group == 'Suspected PE') %>% quantile(height, probs = 0.25, na.rm = TRUE)
## height_suspected_pe_p75     <- filter(dipep, group == 'Suspected PE') %>% quantile(height, probs = 0.75, na.rm = TRUE)
## height_suspected_pe_min     <- filter(dipep, group == 'Suspected PE') %>% min(height, na.rm = TRUE)
## height_suspected_pe_max     <- filter(dipep, group == 'Suspected PE') %>% min(height, na.rm = TRUE)
## height_suspected_pe_missing <- filter(dipep, group == 'Suspected PE' & is.na(height)) %>% nrow()

## Weight
## weight_summary <- dipep_summarise(df     = dipep,
##                                to.sum = weight)
weight_mean    <- mean(dipep$weight, na.rm = TRUE)
weight_sd      <- sd(dipep$weight, na.rm = TRUE)
weight_median  <- quantile(dipep$weight, probs = 0.5, na.rm = TRUE)
weight_p25     <- quantile(dipep$weight, probs = 0.25, na.rm = TRUE)
weight_p75     <- quantile(dipep$weight, probs = 0.75, na.rm = TRUE)
weight_min     <- min(dipep$weight, na.rm = TRUE)
weight_max     <- max(dipep$weight, na.rm = TRUE)
weight_missing <- filter(dipep, is.na(weight)) %>% nrow()
## Weight - Suspected PE
weight_suspected_pe_mean    <- filter(dipep, group == 'Suspected PE') %>% mean(weight, na.rm = TRUE)
## weight_suspected_pe_sd      <- filter(dipep, group == 'Suspected PE') %>% sd(weight, na.rm = TRUE)
## weight_suspected_pe_median  <- filter(dipep, group == 'Suspected PE') %>% quantile(weight, probs = 0.5, na.rm = TRUE)
## weight_suspected_pe_p25     <- filter(dipep, group == 'Suspected PE') %>% quantile(weight, probs = 0.25, na.rm = TRUE)
## weight_suspected_pe_p75     <- filter(dipep, group == 'Suspected PE') %>% quantile(weight, probs = 0.75, na.rm = TRUE)
## weight_suspected_pe_min     <- filter(dipep, group == 'Suspected PE') %>% min(weight, na.rm = TRUE)
## weight_suspected_pe_max     <- filter(dipep, group == 'Suspected PE') %>% min(weight, na.rm = TRUE)
## weight_suspected_pe_missing <- filter(dipep, group == 'Suspected PE' & is.na(weight)) %>% nrow()

## Heart Rate
## heart_rate_summary <- dipep_summarise(df     = dipep,
##                                to.sum = heart.rate)
heart_rate_mean    <- mean(dipep$heart.rate, na.rm = TRUE)
heart_rate_sd      <- sd(dipep$heart.rate, na.rm = TRUE)
heart_rate_median  <- quantile(dipep$heart.rate, probs = 0.5, na.rm = TRUE)
heart_rate_p25     <- quantile(dipep$heart.rate, probs = 0.25, na.rm = TRUE)
heart_rate_p75     <- quantile(dipep$heart.rate, probs = 0.75, na.rm = TRUE)
heart_rate_min     <- min(dipep$heart.rate, na.rm = TRUE)
heart_rate_max     <- max(dipep$heart.rate, na.rm = TRUE)
heart_rate_missing <- filter(dipep, is.na(heart.rate)) %>% nrow()
## Heart Rate - Suspected PE
heart_rate_suspected_pe_mean    <- filter(dipep, group == 'Suspected PE') %>% mean(heart.rate, na.rm = TRUE)
## heart_rate_suspected_pe_sd      <- filter(dipep, group == 'Suspected PE') %>% sd(heart.rate, na.rm = TRUE)
## heart_rate_suspected_pe_median  <- filter(dipep, group == 'Suspected PE') %>% quantile(heart.rate, probs = 0.5, na.rm = TRUE)
## heart_rate_suspected_pe_p25     <- filter(dipep, group == 'Suspected PE') %>% quantile(heart.rate, probs = 0.25, na.rm = TRUE)
## heart_rate_suspected_pe_p75     <- filter(dipep, group == 'Suspected PE') %>% quantile(heart.rate, probs = 0.75, na.rm = TRUE)
## heart_rate_suspected_pe_min     <- filter(dipep, group == 'Suspected PE') %>% min(heart.rate, na.rm = TRUE)
## heart_rate_suspected_pe_max     <- filter(dipep, group == 'Suspected PE') %>% min(heart.rate, na.rm = TRUE)
## heart_rate_suspected_pe_missing <- filter(dipep, group == 'Suspected PE' & is.na(heart.rate)) %>% nrow()

## Respiratory Rate
## respiratory_rate_summary <- dipep_summarise(df     = dipep,
##                                to.sum = respiratory.rate)
respiratory_rate_mean    <- mean(dipep$respiratory.rate, na.rm = TRUE)
respiratory_rate_sd      <- sd(dipep$respiratory.rate, na.rm = TRUE)
respiratory_rate_median  <- quantile(dipep$respiratory.rate, probs = 0.5, na.rm = TRUE)
respiratory_rate_p25     <- quantile(dipep$respiratory.rate, probs = 0.25, na.rm = TRUE)
respiratory_rate_p75     <- quantile(dipep$respiratory.rate, probs = 0.75, na.rm = TRUE)
respiratory_rate_min     <- min(dipep$respiratory.rate, na.rm = TRUE)
respiratory_rate_max     <- max(dipep$respiratory.rate, na.rm = TRUE)
respiratory_rate_missing <- filter(dipep, is.na(respiratory.rate)) %>% nrow()
## Respiratory Rate - Suspected PE
respiratory_rate_suspected_pe_mean    <- filter(dipep, group == 'Suspected PE') %>% mean(respiratory.rate, na.rm = TRUE)
## respiratory_rate_suspected_pe_sd      <- filter(dipep, group == 'Suspected PE') %>% sd(respiratory.rate, na.rm = TRUE)
## respiratory_rate_suspected_pe_median  <- filter(dipep, group == 'Suspected PE') %>% quantile(respiratory.rate, probs = 0.5, na.rm = TRUE)
## respiratory_rate_suspected_pe_p25     <- filter(dipep, group == 'Suspected PE') %>% quantile(respiratory.rate, probs = 0.25, na.rm = TRUE)
## respiratory_rate_suspected_pe_p75     <- filter(dipep, group == 'Suspected PE') %>% quantile(respiratory.rate, probs = 0.75, na.rm = TRUE)
## respiratory_rate_suspected_pe_min     <- filter(dipep, group == 'Suspected PE') %>% min(respiratory.rate, na.rm = TRUE)
## respiratory_rate_suspected_pe_max     <- filter(dipep, group == 'Suspected PE') %>% min(respiratory.rate, na.rm = TRUE)
## respiratory_rate_suspected_pe_missing <- filter(dipep, group == 'Suspected PE' & is.na(respiratory.rate)) %>% nrow()

## Systolic BP
## systolic_summary <- dipep_summarise(df     = dipep,
##                                to.sum = bp.systolic)
systolic_mean    <- mean(dipep$bp.systolic, na.rm = TRUE)
systolic_sd      <- sd(dipep$bp.systolic, na.rm = TRUE)
systolic_median  <- quantile(dipep$bp.systolic, probs = 0.5, na.rm = TRUE)
systolic_p25     <- quantile(dipep$bp.systolic, probs = 0.25, na.rm = TRUE)
systolic_p75     <- quantile(dipep$bp.systolic, probs = 0.75, na.rm = TRUE)
systolic_min     <- min(dipep$bp.systolic, na.rm = TRUE)
systolic_max     <- max(dipep$bp.systolic, na.rm = TRUE)
systolic_missing <- filter(dipep, is.na(bp.systolic)) %>% nrow()
## Systolic BP - Suspected PE
systolic_suspected_pe_mean    <- filter(dipep, group == 'Suspected PE') %>% mean(bp.systolic, na.rm = TRUE)
## systolic_suspected_pe_sd      <- filter(dipep, group == 'Suspected PE') %>% sd(bp.systolic, na.rm = TRUE)
## systolic_suspected_pe_median  <- filter(dipep, group == 'Suspected PE') %>% quantile(bp.systolic, probs = 0.5, na.rm = TRUE)
## systolic_suspected_pe_p25     <- filter(dipep, group == 'Suspected PE') %>% quantile(bp.systolic, probs = 0.25, na.rm = TRUE)
## systolic_suspected_pe_p75     <- filter(dipep, group == 'Suspected PE') %>% quantile(bp.systolic, probs = 0.75, na.rm = TRUE)
## systolic_suspected_pe_min     <- filter(dipep, group == 'Suspected PE') %>% min(bp.systolic, na.rm = TRUE)
## systolic_suspected_pe_max     <- filter(dipep, group == 'Suspected PE') %>% min(bp.systolic, na.rm = TRUE)
## systolic_suspected_pe_missing <- filter(dipep, group == 'Suspected PE' & is.na(bp.systolic)) %>% nrow()

## Diastolic BP
## diastolic_summary <- dipep_summarise(df     = dipep,
##                                to.sum = bp.diastolic)
diastolic_mean    <- mean(dipep$bp.diastolic, na.rm = TRUE)
diastolic_sd      <- sd(dipep$bp.diastolic, na.rm = TRUE)
diastolic_median  <- quantile(dipep$bp.diastolic, probs = 0.5, na.rm = TRUE)
diastolic_p25     <- quantile(dipep$bp.diastolic, probs = 0.25, na.rm = TRUE)
diastolic_p75     <- quantile(dipep$bp.diastolic, probs = 0.75, na.rm = TRUE)
diastolic_min     <- min(dipep$bp.diastolic, na.rm = TRUE)
diastolic_max     <- max(dipep$bp.diastolic, na.rm = TRUE)
diastolic_missing <- filter(dipep, is.na(bp.diastolic)) %>% nrow()
## Diastolic BP - Suspected PE
diastolic_suspected_pe_mean    <- filter(dipep, group == 'Suspected PE') %>% mean(bp.diastolic, na.rm = TRUE)
## diastolic_suspected_pe_sd      <- filter(dipep, group == 'Suspected PE') %>% sd(bp.diastolic, na.rm = TRUE)
## diastolic_suspected_pe_median  <- filter(dipep, group == 'Suspected PE') %>% quantile(bp.diastolic, probs = 0.5, na.rm = TRUE)
## diastolic_suspected_pe_p25     <- filter(dipep, group == 'Suspected PE') %>% quantile(bp.diastolic, probs = 0.25, na.rm = TRUE)
## diastolic_suspected_pe_p75     <- filter(dipep, group == 'Suspected PE') %>% quantile(bp.diastolic, probs = 0.75, na.rm = TRUE)
## diastolic_suspected_pe_min     <- filter(dipep, group == 'Suspected PE') %>% min(bp.diastolic, na.rm = TRUE)
## diastolic_suspected_pe_max     <- filter(dipep, group == 'Suspected PE') %>% min(bp.diastolic, na.rm = TRUE)
## diastolic_suspected_pe_missing <- filter(dipep, group == 'Suspected PE' & is.na(bp.diastolic)) %>% nrow()

## Summary by group
summary.stats <- list()
summary.stats$group       <-  dipep_summarise(df           = dipep,
                                       grouping     = 'group',
                                       group.as.col = TRUE,
                                       age, bmi, heart.rate, bp.systolic, bp.diastolic, height,
                                       weight, respiratory.rate, o2.saturation, gestation)
summary.stats$first.st <- dipep_summarise(df           = dipep,
                      	                  grouping     = 'first.st',
                      	                  group.as.col = TRUE,
                      	                  age, bmi, heart.rate, bp.systolic, bp.diastolic, height,
                      	                  weight, respiratory.rate, o2.saturation, gestation)
summary.stats$second.st <- dipep_summarise(df           = dipep,
                       	                 grouping     = 'second.st',
                       	                 group.as.col = TRUE,
                       	                 age, bmi, heart.rate, bp.systolic, bp.diastolic, height,
                       	                 weight, respiratory.rate, o2.saturation, gestation)
summary.stats$third.st <- dipep_summarise(df           = dipep,
                   	    	          grouping     = 'third.st',
                       	                  group.as.col = TRUE,
                       	                  age, bmi, heart.rate, bp.systolic, bp.diastolic, height,
                       	                  weight, respiratory.rate, o2.saturation, gestation)
summary.stats$fourth.st <- dipep_summarise(df           = dipep,
                    	    	           grouping     = 'fourth.st',
                       	                   group.as.col = TRUE,
                       	                   age, bmi, heart.rate, bp.systolic, bp.diastolic, height,
                       	                   weight, respiratory.rate, o2.saturation, gestation)
summary.biomarkers <- list()
summary.biomarkers$first.st <- dipep_summarise(df           = dipep,
                      	                  grouping     = 'first.st',
                      	                  group.as.col = TRUE,
                      	                  prothombin.time, aprothombin, clauss.fibrinogen, ddimer.innovan,
                                          thrombin.generation.lag.time, thrombin.generation.endogenous.potential,
                                          thrombin.generation.peak, thrombin.generation.time.to.peak,
                                          ddimer.elisa, plasmin.antiplasmin, prothrombin.fragments,
                                          soluble.tissue.factor, troponin,
                                          natriuertic.peptide, mrproanp)
summary.biomarkers$second.st <- dipep_summarise(df           = dipep,
                                                grouping     = 'second.st',
                                                group.as.col = TRUE,
                                                prothombin.time, aprothombin, clauss.fibrinogen, ddimer.innovan,
                                                thrombin.generation.lag.time, thrombin.generation.endogenous.potential,
                                                thrombin.generation.peak, thrombin.generation.time.to.peak,
                                                ddimer.elisa, plasmin.antiplasmin, prothrombin.fragments,
                                                soluble.tissue.factor, troponin,
                                                natriuertic.peptide, mrproanp)
summary.biomarkers$third.st <- dipep_summarise(df           = dipep,
                                               grouping     = 'third.st',
                                               group.as.col = TRUE,
                                               prothombin.time, aprothombin, clauss.fibrinogen, ddimer.innovan,
                                               thrombin.generation.lag.time, thrombin.generation.endogenous.potential,
                                               thrombin.generation.peak, thrombin.generation.time.to.peak,
                                               ddimer.elisa, plasmin.antiplasmin, prothrombin.fragments,
                                               soluble.tissue.factor, troponin,
                                               natriuertic.peptide, mrproanp)
summary.biomarkers$fourth.st <- dipep_summarise(df           = dipep,
                                                grouping     = 'fourth.st',
                                                group.as.col = TRUE,
                                                prothombin.time, aprothombin, clauss.fibrinogen, ddimer.innovan,
                                                thrombin.generation.lag.time, thrombin.generation.endogenous.potential,
                                                thrombin.generation.peak, thrombin.generation.time.to.peak,
                                                ddimer.elisa, plasmin.antiplasmin, prothrombin.fragments,
                                                soluble.tissue.factor, troponin,
                                                natriuertic.peptide, mrproanp)

```

#### Ethnicity

Of the `r n_screened` individuals screened `r n_ethnicity` unique ethnicities were recorded for `r nonmissing_ethnicity` individuals and was missing for `r missing_ethnicity` individuals.  Table  details the frequency of recorded ethnicities and these are plotted in figure

```{r  demographics_table_ethnicity, echo = FALSE, cache = FALSE, results = 'markup', eval = FALSE}
kable(ethnicity, group)
```

```{r  demographics_figure_ethnicity, echo = FALSE, cache = FALSE, results = 'hide', fig.width = 10, eval = TRUE}
dplyr::select(dipep, ethnicity, group) %>%
    ggplot(aes(x    = ethnicity,
               fill = ethnicity)) +
    geom_bar() +
    xlab('') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~group, ncol = 3) + theme_bw() +
    theme(axis.text.x = element_text(angle = 90))

```


#### Age

The overall mean age in years of those was `r age_mean` (SD `r age_sd`; Median `r age_median` (IQR `r age_p25` to `r age_p75`); Range `r age_min` to `r age_max`) and the distribution of ages by group is summarised in figure and table below.

```{r  demographics_figure_age_group, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, age, group) %>%
    ggplot(aes(x    = age,
               fill = group)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Age (Years)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~group, ncol = 3) + theme_bw()
dplyr::filter(summary.stats$group, Measurement == 'Age') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Age by Recruitment Group')
```

```{r  demographics_figure_age_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, age, first.st) %>%
    mutate(first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                             no  = first.st)) %>%
    ggplot(aes(x    = age,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Age (Years)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.stats$first.st, Measurement == 'Age') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Age by Primary Classification')


```

#### BMI

The overall mean BMI was `r bmi_mean` (SD `r bmi_sd`; Median `r bmi_median` (IQR `r bmi_p25` to `r bmi_p75`); Range `r bmi_min` to `r bmi_max`) and the distribution of BMI by group is summarised in figure and table below.


```{r  demographics_figure_bmi_group, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, bmi, group) %>%
    ggplot(aes(x    = bmi,
               fill = group)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('BMI') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~group, ncol = 3) + theme_bw()
dplyr::filter(summary.stats$group, Measurement == 'BMI') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of BMI by Recruitment Group')


```

```{r  demographics_figure_bmi_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, bmi, first.st) %>%
    mutate(first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                             no  = first.st)) %>%
    ggplot(aes(x    = bmi,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('BMI') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.stats$first.st, Measurement == 'BMI') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of BMI by Primary Classification')


```

#### Height

The overall mean height in centimetres (cm) was `r height_mean` (SD `r height_sd`; Median `r height_median` (IQR `r height_p25` to `r height_p75`); Range `r height_min` to `r height_max`) and the distribution of heights by group is summarised in figure and table below.


```{r  demographics_figure_height_group, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, height, group) %>%
    ggplot(aes(x    = height,
               fill = group)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Height (cm)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~group, ncol = 3) + theme_bw()
dplyr::filter(summary.stats$group, Measurement == 'Height') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Height by Recruitment Group')

```

```{r  demographics_figure_height_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, height, first.st) %>%
    mutate(first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                                  no  = first.st)) %>%
    ggplot(aes(x    = height,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Height (cm)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.stats$first.st, Measurement == 'Height') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Height by Primary Classification')

```

#### Weight

The mean weight in kilgrams (kg) was `r weight_mean` (SD `r weight_sd`; Median `r weight_median` (IQR `r weight_p25` to `r weight_p75`); Range `r weight_min` to `r weight_max`) and the distribution of weights by group is summarised in figure and table below.


```{r  demographics_figure_weight_group, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, weight, group) %>%
    ggplot(aes(x    = weight,
               fill = group)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Weight (kg)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~group, ncol = 3) + theme_bw()
dplyr::filter(summary.stats$group, Measurement == 'Weight') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Weight by Recruitment Group')

```

```{r  demographics_figure_weight_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, weight, first.st) %>%
    mutate(first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                                  no  = first.st)) %>%
    ggplot(aes(x    = weight,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Weight (kg)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.stats$first.st, Measurement == 'Weight') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Weight by Primary Classification')

```

#### Heart Rate

The overall mean heart rate in beats per minute (BPM) was `r heart_rate_mean` (SD `r heart_rate_sd`; Median `r heart_rate_median` (IQR `r heart_rate_p25` to `r heart_rate_p75`); Range `r heart_rate_min` to `r heart_rate_max`) and the distribution of weights by group is summarised in figure and table below.


```{r  demographics_figure_heart_rate_group, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, heart.rate, group) %>%
    ggplot(aes(x    = heart.rate,
               fill = group)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Heart Rate (BPM)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~group, ncol = 3) + theme_bw()
dplyr::filter(summary.stats$group, Measurement == 'Respiratory Rate') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Respiratory Rate by Recruitment Group')

```

```{r  demographics_figure_heart_rate_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, heart.rate, first.st) %>%
    mutate(first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                                  no  = first.st)) %>%
    ggplot(aes(x    = heart.rate,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Heart Rate (BPM)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.stats$first.st, Measurement == 'Respiratory Rate') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Respiratory Rate by Primary Classification')

```


#### Respiratory Rate

The overall mean respiratory rate in breaths per minute (BPM) was `r respiratory_rate_mean` (SD `r respiratory_rate_sd`; Median `r respiratory_rate_median` (IQR `r respiratory_rate_p25` to `r respiratory_rate_p75`); Range `r respiratory_rate_min` to `r respiratory_rate_max`) and the distribution of weights by group is summarised in figure and table below.


```{r  demographics_figure_respiratory_rate_group, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, respiratory.rate, group) %>%
    ggplot(aes(x    = respiratory.rate,
               fill = group)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Respiratory Rate (BPM)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~group, ncol = 3) + theme_bw()
dplyr::filter(summary.stats$group, Measurement == 'Respiratory Rate') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Respiratory Rate (BPM) by Recruitment Group')

```

```{r  demographics_figure_respiratory_rate_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, respiratory.rate, first.st) %>%
    mutate(first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                                  no  = first.st)) %>%
    ggplot(aes(x    = respiratory.rate,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Respiratory Rate (BPM)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.stats$first.st, Measurement == 'Respiratory Rate') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Respiratory Rate (BPM) by Primary Classification')

```

#### Systolic Blood Pressure

The overall mean systolic blood pressure in millimetres of mercury (mmHg) was `r systolic_mean` (SD `r systolic_sd`; Median `r systolic_median` (IQR `r systolic_p25` to `r systolic_p75`); Range `r systolic_min` to `r systolic_max`) and the distribution of weights by group is summarised in figure and table below.


```{r  demographics_figure_systolic_group, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, bp.systolic, group) %>%
    ggplot(aes(x    = bp.systolic,
               fill = group)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Systolic Blood Pressure (mm/Hg)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~group, ncol = 3) + theme_bw()
dplyr::filter(summary.stats$group, Measurement == 'Systolic BP') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Systolic Blood Pressure (mm/Hg) by Recruitment Group')

```

```{r  demographics_figure_systolic_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, bp.systolic, first.st) %>%
    mutate(first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                                  no  = first.st)) %>%
    ggplot(aes(x    = bp.systolic,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Systolic Blood Pressure (mm/Hg)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.stats$first.st, Measurement == 'Systolic BP') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Systolic Blood Pressure (mm/Hg) by Primary Classification')

```

#### Diastolic Blood Pressure

The overall mean diastolic blood pressure in millimetres of mercury (mmHg) was `r diastolic_mean` (SD `r diastolic_sd`; Median `r diastolic_median` (IQR `r diastolic_p25` to `r diastolic_p75`); Range `r diastolic_min` to `r diastolic_max`) and the distribution of weights by group is summarised in figure and table below.


```{r  demographics_figure_diastolic_group, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, bp.diastolic, group) %>%
    ggplot(aes(x    = bp.diastolic,
               fill = group)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Diastolic Blood Pressure (mm/Hg)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~group, ncol = 3) + theme_bw()
dplyr::filter(summary.stats$group, Measurement == 'Diastolic BP') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Diastolic Blood Pressure (mm/Hg) by Recruitment Group')

```

```{r  demographics_figure_diastolic_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, bp.diastolic, first.st) %>%
    mutate(first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                                  no  = first.st)) %>%
    ggplot(aes(x    = bp.diastolic,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Diastolic Blood Pressure (mm/Hg)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.stats$first.st, Measurement == 'Diastolic BP') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Diastolic Blood Pressure (mm/Hg) by Primary Classification')

```

#### Oxygen Saturation

The overall mean oxygen saturation as a percentage (%) was `r diastolic_mean` (SD `r diastolic_sd`; Median `r diastolic_median` (IQR `r diastolic_p25` to `r diastolic_p75`); Range `r diastolic_min` to `r diastolic_max`) and the distribution of weights by group is summarised in figure and table below.


```{r  demographics_figure_o2_saturation_group, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, o2.saturation, group) %>%
    ggplot(aes(x    = o2.saturation,
               fill = group)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Oxygen Saturation (mm/Hg)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~group, ncol = 3) + theme_bw()
dplyr::filter(summary.stats$group, Measurement == 'Oxygen Saturation') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Oxygen Saturation by Recruitment Group')

```

```{r  demographics_figure_o2_saturation_primary_class, echo = FALSE, cache = FALSE, results = 'markup', warning = FALSE, fig.width = 10, eval = TRUE}
dplyr::select(dipep, o2.saturation, first.st) %>%
    mutate(first.st = ifelse(is.na(first.st),
                                  yes = 'Exclude',
                                  no  = first.st)) %>%
    ggplot(aes(x    = o2.saturation,
               fill = first.st)) +
    geom_histogram() +
    ## stat_bin(binwidth = ggplot2.opts$binwidth) +
    xlab('Oxygen Saturation (mm/Hg)') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    theme(axis.text.x = element_text(angle = 90)) +
    facet_wrap(~first.st, ncol = 3) + theme_bw()
dplyr::filter(summary.stats$first.st, Measurement == 'Oxygen Saturation') %>%
    dplyr::select(-Measurement) %>%
    kable(caption = 'Summary of Oxygen Saturation by Primary Classification')

```
