```{r recruitment_summary, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
## Save useful numbers for use in text
n_centers       <- unique(master$womans.details$site) %>% length()
n_screened      <- nrow(master$womans.details)
n_diagnosed_dvt <- filter(master$womans.details, group == 'Diagnosed DVT') %>% nrow()
n_non_recruited <- filter(master$womans.details, group == 'Non recruited') %>% nrow()
n_suspected_pe  <- filter(master$womans.details, group == 'Suspected PE') %>% nrow()
n_missing_recruitment_date <- filter(master$womans.details, is.na(event.date)) %>% nrow()
```
Patients were recruited `r n_centers` across the UK.  Of these `r n_diagnosed_dvt` were diagnosed with DVT, `r n_suspected_pe` were suspected of having PE and `r n_non_recruited` were not recruited.  Table  shows the numbers by center and these are shown graphically in figure

```{r recrutiment_by_center, echo = FALSE, cache = FALSE, results = 'markup', eval = FALSE}
table(master$womans.details$site, master$womans.details$group) %>%
kable()
```

```{r recrutiment_by_center, echo = FALSE, cache = FALSE, results = 'markup', fig.width = 10, eval = TRUE}
## Subset out data for plotting
dplyr::select(master$womans.details, site, group) %>%
    ggplot(aes(x    = group,
               fill = group)) +
    geom_bar() +
    xlab('') + ylab('N') +
    guides(fill = guide_legend(NULL)) +
    facet_wrap(~site, ncol = 3) +
    theme_bw()

```

**NB** It is not possible to screening rates of non-recruited individuals since the date is not recorded (`event.dates` are acutally missing and instead baseline date is the `consent.date`).

```{r recrutiment_rate_by_center, echo = FALSE, cache = FALSE, results = 'markup', fig.width = 10, eval = TRUE}
dplyr::select(dipep, event.date, group, site) %>%
    group_by(site, group) %>%
    arrange(site, group, event.date) %>%
    mutate(n = 1,
           recruited = cumsum(n)) %>%
    filter(group != 'Non recruited') %>%
    ggplot(aes(x     = event.date,
               y     = recruited,
               color = group)) +
    geom_line() +
    xlab('Date') + ylab('N') +
    guides(fill = guide_legend('Group')) +
    facet_wrap(~site, ncol = 3)

```

**TODO** Rotate x-axis labels
