### LASSO



```{r results_lasso_save, echo = FALSE, cache = FALSE, results = 'hide', eval = FALSE}
save(lasso.categorical, cv.lasso.categorical,
     lasso.continuous, cv.lasso.continuous,
     file = '../../data/results/lasso.RData')

```
```{r results_lasso_load, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
load(file = '../../data/results/lasso.RData')

```

The [LASSO (Least Absolute Shrinkage and Selection Operator)](https://en.wikipedia.org/wiki/Lasso_(statistics)) is a method of automated selection of covariates/predictor variables that maximises the accuracy of the model without inflating the estimated coefficients for each variable.  The [R](https://www.r-project.org/) package [glmnet](https://cran.r-project.org/web/packages/glmnet/) has been used to fit a model using the LASSO and if you are interested in learning about the LASSO or fitting with this model it is recommended you read the packages [vignette](https://cran.r-project.org/web/packages/glmnet/vignettes/glmnet\_beta.html), in particular the section on logistic regression.

#### Model {.tabset .tabset-fade .tabset-pills}

The model that has been fitted uses the outcome variable of the observed events of Pulmonary Embolisms in the recruited cohort of Suspected PE individuals.  A large number of predictor variables are used initially (although in doing so caution should be used in interpretting the results because the cohort is quite small in the context of fitting such models).  The model takes the general form...

$$
pulmonary embolism classification ~ predictors
$$

Exactly what predictors are included/used in a model varies.  Strictly the Statistical Analysis Plan states that may of the continuous physiological variables are to be dichotomised prior to analysis.  This is however not advisable for [various reasons]()(@altman2006,  @royston2006, @dawson2012), in particular @steyerberg2001 demonstrated that doing so results in a reduction in available information in the setting of prognostic modelling.  To this end the models have been tested using the raw continuous variables as well.

<!-- The plot below shows the change in the coefficients for each predictor variable over iterations of estimation via LASSO. L1 Norm is a constraint placed on the analsyis for the sum of all coefficients and is one of the unique features of the LASSO.  For further details on L1 normalisation please refer to [this article](http://people.duke.edu/~hpgavin/SystemID/References/Schmidt-LASSO-2005.pdf). -->


```{r child='lasso/categorised.Rmd', eval = TRUE}
```

```{r child='lasso/continuous.Rmd', eval = TRUE}
```

```{r child='lasso/staged.Rmd', eval = TRUE}
```
