```{r results_existing, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
```

#### PERC Score

The PERC Score for study participants (@kline2004) is summarised below.  It should be noted though that the PERC score is designed to be used when a diagnosis of PE is being considered but the risk is low (as described in the [online calculator](http://www.mdcalc.com/perc-rule-pulmonary-embolism/)), which is not the case in the cohort being considered in this study.

```{r results_existing_perc, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
ggplot(dipep, aes(x = perc)) +
    geom_bar(aes(fill = pe), position = 'dodge') +
    ggtitle('PERC Scores by clinical classification') +
    xlab('PERC Score') + ylab('N') +
    scale_fill_discrete(guide = guide_legend(title = 'Status')) +
    theme_bw()
## kable(dipep$pe, dipep$perc, caption = 'Tabulation of PERC Score by clinical classification')

```

#### Simplified Revised Geneva
```{r results_existing_simplified_revised_geneva, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
ggplot(dipep, aes(x = simplified)) +
    geom_bar(aes(fill = pe), position = 'dodge') +
    ggtitle('Simplified Revised Geneva  Scores by clinical classification') +
    xlab('PERC Score') + ylab('N') +
    scale_fill_discrete(guide = guide_legend(title = 'Status')) +
    theme_bw()

```

#### Wells Score

The Wells Score (@wells2001) is summarised below.

```{r results_existing_wells, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
ggplot(dipep, aes(x = wells)) +
    geom_bar(aes(fill = pe), position = 'dodge') +
    ggtitle('PERC Scores by clinical classification') +
    xlab('PERC Score') + ylab('N') +
    scale_fill_discrete(guide = guide_legend(title = 'Status')) +
    theme_bw()
## kable(dipep$pe, dipep$wells, caption = 'Tabulation of Wells Score by clinical classification')

```
