Its is not advisable to use the results of univariable regression to shape your choice of variables to include in multi-variable models for the simple reason that the coefficients obtained for a variable in isolation will not be the same as those from a multi-variable model.  Thus something that appears to be significant under univariable analysis may well not be under multi-variable analysis.  A better strategy is to use expert clinical knowledge as to what factors are important to determine which variables are included in a multi-variable model.

Regardless each of the individual variables has been analysed under a univariable logistic regression model.  The coefficients, their confidence intervals, the sensitivity, specificity and area under the receiver operating characeristics curve are tabulated below.

```{r results_logistic_regression, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
## Test each outcome for association, then gather them *using broom) into one dataset for summarisation
## Age
logistic.age <- dipep_glm(df = dipep,
                          predictor = 'age')
## Age (Categorised)
logistic.age.cat <- dipep_glm(df = dipep,
                          predictor = 'age.cat')
## Smoking
logistic.smoking <- dipep_glm(df = dipep,
                          predictor = 'smoking')
## Temperature (Categorised)
logistic.temperature.cat <- dipep_glm(df = dipep,
                          predictor = 'temperature.cat')
## Temperature
logistic.temperature <- dipep_glm(df = dipep,
                          predictor = 'temperature')
## BP Diastolic (Categorised)
logistic.bp.diastolic.cat <- dipep_glm(df = dipep,
                          predictor = 'bp.diastolic.cat')
## BP Diastolic
logistic.bp.diastolic <- dipep_glm(df = dipep,
                          predictor = 'bp.diastolic')
## BP Systolic (Categorised)
## logistic.bp.systolic.cat <- dipep_glm(df = dipep,
##                           predictor = 'bp.systolic.cat')
## BP Systolic
logistic.bp.systolic <- dipep_glm(df = dipep,
                          predictor = 'bp.systolic')
## O2 Saturation (Categorised)
logistic.o2.saturation.cat <- dipep_glm(df = dipep,
                          predictor = 'o2.saturation.cat')
## O2 Saturation
logistic.o2.saturation <- dipep_glm(df = dipep,
                          predictor = 'o2.saturation')
## Respiratory Rate (Categorised)
logistic.respiratory.rate.cat <- dipep_glm(df = dipep,
                          predictor = 'respiratory.rate.cat')
## Respiratory Rate
logistic.respiratory.rate <- dipep_glm(df = dipep,
                          predictor = 'respiratory.rate')
## BMI (Categorised)
logistic.bmi.cat <- dipep_glm(df = dipep,
                          predictor = 'bmi.cat')
## BMI
logistic.bmi <- dipep_glm(df = dipep,
                          predictor = 'bmi')
## Previous Pregnancies < 24 weeks
logistic.pregnancies.under <- dipep_glm(df = dipep,
                          predictor = 'pregnancies.under')
## Previous Pregnancies > 24 weeks
logistic.pregnancies.over <- dipep_glm(df = dipep,
                          predictor = 'pregnancies.over')
## Previous Pregnancy Problems
logistic.prev.preg.problem <- dipep_glm(df = dipep,
                             predictor = 'prev.preg.problem')
## For now fill in missing, will switch to using 'imputed' data set later
dipep <- mutate(dipep,
                presenting.features.pleuritic = ifelse(is.na(presenting.features.pleuritic),
                                                       yes = 'Not Ticked',
                                                       no  = presenting.features.pleuritic),
                presenting.features.non.pleuritic = ifelse(is.na(presenting.features.non.pleuritic),
                                                       yes = 'Not Ticked',
                                                       no  = presenting.features.non.pleuritic),
                presenting.features.sob.exertion = ifelse(is.na(presenting.features.sob.exertion),
                                                       yes = 'Not Ticked',
                                                       no  = presenting.features.sob.exertion),
                presenting.features.sob.rest = ifelse(is.na(presenting.features.sob.rest),
                                                       yes = 'Not Ticked',
                                                       no  = presenting.features.sob.rest),
                presenting.features.haemoptysis = ifelse(is.na(presenting.features.haemoptysis),
                                                       yes = 'Not Ticked',
                                                       no  = presenting.features.haemoptysis),
                presenting.features.cough = ifelse(is.na(presenting.features.cough),
                                                       yes = 'Not Ticked',
                                                       no  = presenting.features.cough),
                presenting.features.syncope = ifelse(is.na(presenting.features.syncope),
                                                       yes = 'Not Ticked',
                                                       no  = presenting.features.syncope),
                presenting.features.palpitations = ifelse(is.na(presenting.features.palpitations),
                                                       yes = 'Not Ticked',
                                                       no  = presenting.features.palpitations),
                presenting.features.other = ifelse(is.na(presenting.features.other),
                                                       yes = 'Not Ticked',
                                                       no  = presenting.features.other))
## Pleuritic
logistic.presenting.features.pleuritic <- dipep_glm(df = dipep,
                          predictor = 'presenting.features.pleuritic')
## Non-Pleuritic
logistic.presenting.features.non.pleuritic <- dipep_glm(df = dipep,
                          predictor = 'presenting.features.non.pleuritic')
## Shortness of Breath (Exertion)
logistic.presenting.features.sob.exertion <- dipep_glm(df = dipep,
                          predictor = 'presenting.features.sob.exertion')
## Shortness of Breath (Rest)
logistic.presenting.features.sob.rest <- dipep_glm(df = dipep,
                          predictor = 'presenting.features.sob.rest')
## Haemoptysis
logistic.presenting.features.haemoptysis <- dipep_glm(df = dipep,
                          predictor = 'presenting.features.haemoptysis')
## Cough
logistic.presenting.features.cough <- dipep_glm(df = dipep,
                          predictor = 'presenting.features.cough')
## Syncope
logistic.presenting.features.syncope <- dipep_glm(df = dipep,
                          predictor = 'presenting.features.syncope')
## Palpitations
logistic.presenting.features.palpitations <- dipep_glm(df = dipep,
                          predictor = 'presenting.features.palpitations')
## Other Features on Presentation
logistic.presenting.features.other <- dipep_glm(df = dipep,
                          predictor = 'presenting.features.other')

## Combine all three sets of tidied output from each model
logistic.tidied <- rbind(logistic.age$tidied,
                         logistic.age.cat$tidied,
                         logistic.smoking$tidied,
                         logistic.temperature.cat$tidied,
                         logistic.temperature$tidied,
                         logistic.bp.diastolic.cat$tidied,
                         logistic.bp.diastolic$tidied,
                         ## logistic.bp.systolic.cat$tidied,
                         logistic.bp.systolic$tidied,
                         logistic.o2.saturation.cat$tidied,
                         logistic.o2.saturation$tidied,
                         logistic.respiratory.rate.cat$tidied,
                         logistic.respiratory.rate$tidied,
                         logistic.bmi.cat$tidied,
                         logistic.bmi$tidied,
                         logistic.pregnancies.under$tidied,
                         logistic.pregnancies.over$tidied,
                         logistic.prev.preg.problem$tidied,
                         logistic.presenting.features.pleuritic$tidied,
                         logistic.presenting.features.non.pleuritic$tidied,
                         logistic.presenting.features.sob.exertion$tidied,
                         logistic.presenting.features.sob.rest$tidied,
                         logistic.presenting.features.haemoptysis$tidied,
                         logistic.presenting.features.cough$tidied,
                         logistic.presenting.features.syncope$tidied,
                         logistic.presenting.features.palpitations$tidied,
                         logistic.presenting.features.other$tidied) %>%
                    mutate(term = gsub('age.catOld', 'Age (Old)', term),
                           term = gsub('smokinggave up prior to pregnancy', 'Ex-smoker (Prior)', term),
                           term = gsub('smokinggave up during pregnancy', 'Ex-smoker (During)', term),
                           term = gsub('smokingcurrent', 'Current Smoker', term),
                           term = gsub('temperature.catHigh', 'Temperature (High)', term),
                           term = gsub('bp.diastolic.catHigh', 'Diastolic (High)', term),
                           term = gsub('bp.systolic.catHigh', 'Systolic (High)', term),
                           term = gsub('o2.saturation.catHigh', 'O2 Saturation (High)', term),
                           term = gsub('respiratory.rate.catHigh', 'Respiratory Rate (High)', term),
                           term = gsub('bmi.catHigh', 'BMI (High)', term),
                           term = gsub('Ticked', '', term),
                           ## term = gsub('.cat', ' (Categorised)', term),
                           term = gsub('age', 'Age (Continuous)', term),
                           term = gsub('bp.diastolic', 'Diastolic (Continuous)', term),
                           term = gsub('bp.systolic', 'Systolic (Continuous)', term),
                           term = gsub('o2.saturation', 'O2 Saturation (Continuous)', term),
                           term = gsub('bmi', 'BMI (Continuous)', term),
                           term = gsub('presenting.features.pleuritic', 'True', term),
                           term = gsub('presenting.features.non.pleuritic', 'True', term),
                           term = gsub('presenting.features.sob.exertion', 'True', term),
                           term = gsub('presenting.features.sob.rest', 'True', term),
                           term = gsub('presenting.features.haemoptysis', 'True', term),
                           term = gsub('presenting.features.cough', 'True', term),
                           term = gsub('presenting.features.syncope', 'True', term),
                           term = gsub('presenting.features.palpitations', 'True', term),
                           term = gsub('presenting.features.other', 'True', term)) %>%
                    mutate(lower = estimate - 1.96 * std.error,
                           upper = estimate + 1.96 * std.error)

logistic.glance <- rbind(logistic.age$glance,
                         logistic.smoking$glance,
                         logistic.temperature.cat$glance,
                         logistic.temperature$glance,
                         logistic.bp.diastolic.cat$glance,
                         logistic.bp.diastolic$glance,
                         ## logistic.bp.systolic.cat$glance,
                         logistic.bp.systolic$glance,
                         logistic.o2.saturation.cat$glance,
                         logistic.o2.saturation$glance,
                         logistic.respiratory.rate.cat$glance,
                         logistic.respiratory.rate$glance,
                         logistic.bmi.cat$glance,
                         logistic.bmi$glance,
                         logistic.pregnancies.under$glance,
                         logistic.pregnancies.over$glance,
                         logistic.prev.preg.problem$glance,
                         logistic.presenting.features.pleuritic$glance,
                         logistic.presenting.features.non.pleuritic$glance,
                         logistic.presenting.features.sob.exertion$glance,
                         logistic.presenting.features.sob.rest$glance,
                         logistic.presenting.features.haemoptysis$glance,
                         logistic.presenting.features.cough$glance,
                         logistic.presenting.features.syncope$glance,
                         logistic.presenting.features.palpitations$glance,
                         logistic.presenting.features.other$glance)
## Get all predicted values
logistic.predicted <- merge(logistic.age$predicted,
                            logistic.age.cat$predicted,
                            by  = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.smoking$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.temperature$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.temperature.cat$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.bp.diastolic$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.bp.diastolic.cat$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.bp.systolic$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      ## merge(.,
                      ##       logistic.bp.systolic.cat$predicted,
                      ##       by = 'obs',
                      ##       all = TRUE) %>%
                      merge(.,
                            logistic.o2.saturation$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.o2.saturation.cat$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.respiratory.rate$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.respiratory.rate.cat$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.bmi$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.bmi.cat$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.pregnancies.under$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.pregnancies.over$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.prev.preg.problem$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.presenting.features.pleuritic$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.presenting.features.non.pleuritic$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.presenting.features.sob.rest$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.presenting.features.sob.exertion$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.presenting.features.haemoptysis$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.presenting.features.cough$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.presenting.features.syncope$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.presenting.features.palpitations$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      merge(.,
                            logistic.presenting.features.other$predicted,
                            by = 'obs',
                            all = TRUE) %>%
                      ## Age is complete, use observed values from that, remove all others
                      dplyr::select(pe.age, pred.age, pred.age.cat, pred.smoking,
                                    pred.temperature, pred.temperature.cat,
                                    pred.bp.diastolic, pred.bp.diastolic.cat,
                                    pred.bp.systolic, ## pred.bp.systolic.cat,
                                    pred.o2.saturation, pred.o2.saturation.cat,
                                    pred.respiratory.rate, pred.respiratory.rate.cat,
                                    pred.bmi, pred.bmi.cat, pred.prev.preg.problem,
                                    pred.pregnancies.under, pred.pregnancies.over,
                                    pred.presenting.features.pleuritic, pred.presenting.features.non.pleuritic,
                                    pred.presenting.features.sob.rest, pred.presenting.features.sob.exertion,
                                    pred.presenting.features.cough, pred.presenting.features.haemoptysis,
                                    pred.presenting.features.syncope, pred.presenting.features.palpitations,
                                    pred.presenting.features.other)
## Sort out names
names(logistic.predicted) <- gsub('pe.age', 'pe', names(logistic.predicted))
names(logistic.predicted) <- gsub('pred.', '', names(logistic.predicted))

## ToDo - Possibly add in descriptive labels (perhaps build a dataframe with these to make it easy)
```

#### Point Estimates

The point-estimate and
```{r results_logistic_regression_summary, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
to.sum <- dplyr::filter(logistic.tidied, term != '(Intercept)') %>%
    dplyr::select(predictor, term, estimate, lower, upper, p.value)
ggplot(to.sum, aes(predictor, estimate, colour = predictor)) +
    geom_point() + geom_errorbar(aes(ymin =lower, ymax = upper)) +
    coord_flip() +
    xlab('Predictor') + ylab('Estimate') +
    ggtitle('Point Estimate and 95% CI for Univariable Logistic Regression') +
    theme_bw() + theme(legend.position = 'none')
names(to.sum) <- c('Predictor', 'Level', ' Estimate', 'Lower CI', 'Upper CI', 'P-Value')
kable(to.sum,
      caption = 'Point estimates, 95% CIs and p-values for Univariable Regression')
rm(to.sum)

```
#### ROC Curves

[Sensitivity and Specificity](https://en.wikipedia.org/wiki/Sensitivity_and_specificity) are not absolute since each individual is assigned a probability from the logistic regression model and it is then down to the investigator to decide what threshold ($0 < x < 1$) should be used to classify someone as having a Pulmonary Embolism.  A simple way of visualising the sensitivity and specificity for different thresholds is via a [Receiver Operating Characteristic Curve](https://en.wikipedia.org/wiki/Receiver_operating_characteristic) which plots the [false-positive rate](https://en.wikipedia.org/wiki/False_positive_rate) against the true positive rate.  The following graph shows the curves for the different univariable logistic regression models.

```{r results_logistic_regression_roc, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
## This uses the geom_roc() ggplot2 extension from the ploROC package
markers <- names(logistic.predicted)[2:length(names(logistic.predicted))]
to.plot <- melt_roc(logistic.predicted, d = 'pe', m = markers)
to.plot <- mutate(to.plot,
                  name = gsub('presenting.features.', '', name))
## names(to.plot) <- gsub('name', 'Predictor', names(to.plot)
## ROC for continuous variables
ggplot(dplyr::filter(to.plot, name %in% c('age', 'bmi', 'o2.saturation', 'bp.diastolic', 'bp.systolic', 'temperature')),
       aes(d = D, m = M, color = name)) +
    geom_roc() +
    guides(guide = guide_legend(title = 'Predictor...')) +
    ggtitle('ROC curves for Continuous Univariable Logistic Regression') +
    style_roc() + theme_bw()
## Plot categorised variables
ggplot(dplyr::filter(to.plot, name %in% c('age.cat', 'bmi.cat', 'o2.saturation.cat', 'bp.diastolic.cat', 'bp.systolic.cat', 'temperature.cat')),
       aes(d = D, m = M, color = name)) +
    geom_roc() +
    guides(guide = guide_legend(title = 'Predictor...')) +
    ggtitle('ROC curves for Binary Univariable Logistic Regression') +
    style_roc() + theme_bw()
## Plot presenting features
ggplot(dplyr::filter(to.plot, name %in% c('pleuritic',
                                          'non.pleuritic',
                                          'sob.exertion',
                                          'sob.rest',
                                          'cough',
                                          'haemoptysis',
                                          'syncope',
                                          'palpitations',
                                          'other')),
       aes(d = D, m = M, color = name)) +
    geom_roc() +
    guides(guide = guide_legend(title = 'Predictor...')) +
    ggtitle('ROC curves for Presenting Features Univariable Logistic Regression') +
    style_roc() + theme_bw()
## Plot Other
ggplot(dplyr::filter(to.plot, name %in% c('prev.preg.problem',
                                          'pregnancies.over',
                                          'pregnancies.under')),
       aes(d = D, m = M, color = name)) +
    geom_roc() +
    guides(guide = guide_legend(title = 'Predictor...')) +
    ggtitle('ROC curves for Presenting Features Univariable Logistic Regression') +
    style_roc() + theme_bw()

```
