### Biomarkers {.tabset .tabset-fade .tabset-pills}

```{r biomarkers_logistic, echo = FALSE, cache = FALSE, message = FALSE, results = 'hide', eval = TRUE}
## Test association of each biomarker
biomarker <- list()
## Prothombin (Time)
biomarker$prothombin.time <- dipep_glm(df = dipep,
                                       classification = 'first.st',
                                       predictor      = 'prothombin.time',
                                       model          = 'Prothombin (Time)')
## Aprothombin
biomarker$aprothombin <- dipep_glm(df = dipep,
                                   classification = 'first.st',
                                   predictor      = 'aprothombin',
                                   model          = 'Aprothombin')
## Claus Fibrinogen
biomarker$clauss.fibrinogen <- dipep_glm(df = dipep,
                                         classification = 'first.st',
                                         predictor      = 'clauss.fibrinogen',
                                         model          = 'Clauss Fibrinogen')
## D-Dimer - Innovan
biomarker$ddimer.innovan <- dipep_glm(df = dipep,
                                         classification = 'first.st',
                                         predictor      = 'ddimer.innovan',
                                         model          = 'D-Dimer (Innovan)')
## D-Dimer - ELISA
biomarker$ddimer.elisa <- dipep_glm(df = dipep,
                                         classification = 'first.st',
                                         predictor      = 'ddimer.elisa',
                                         model          = 'D-Dimer (ELISA)')
# Thombin Generation - Lag Time
biomarker$thrombin.generation.lag.time <- dipep_glm(df = dipep,
                                                    classification = 'first.st',
                                                    predictor      = 'thrombin.generation.lag.time',
                                                    model          = 'Thrombin Generation (Lag Time)')
# Thombin Generation - Endogenous Potential
biomarker$thrombin.generation.endogenous.potential <- dipep_glm(df = dipep,
                                                    classification = 'first.st',
                                                    predictor      = 'thrombin.generation.endogenous.potential',
                                                    model          = 'Thrombin Generation (Endogenous Potential)')
# Thombin Generation - Peak
biomarker$thrombin.generation.peak <- dipep_glm(df = dipep,
                                                classification = 'first.st',
                                                predictor      = 'thrombin.generation.peak',
                                                model          = 'Thrombin Generation (Peak)')
# Thombin Generation - Time to Peak
biomarker$thrombin.generation.time.to.peak <- dipep_glm(df = dipep,
                                                classification = 'first.st',
                                                predictor      = 'thrombin.generation.time.to.peak',
                                                model          = 'Thrombin Generation (Time to Peak)')
# Plasmin - Antiplasmin
biomarker$plasmin.antiplasmin <- dipep_glm(df = dipep,
                                           classification = 'first.st',
                                           predictor      = 'plasmin.antiplasmin',
                                           model          = 'Plasmin (Antiplasmin)')
# Prothombin Fragments
biomarker$prothrombin.fragments <- dipep_glm(df = dipep,
                                             classification = 'first.st',
                                             predictor      = 'prothrombin.fragments',
                                             model          = 'Prothombin Fragments')
# Soluble Tissue Factor
biomarker$soluble.tissue.factor <- dipep_glm(df = dipep,
                                             classification = 'first.st',
                                             predictor      = 'soluble.tissue.factor',
                                             model          = 'Soluble Tissue Factor')
# Troponin
biomarker$troponin <- dipep_glm(df = dipep,
                                classification = 'first.st',
                                predictor      = 'troponin',
                                model          = 'Troponin')
## # Natriuertic Peptide
biomarker$natriuertic.peptide <- dipep_glm(df = dipep,
                                           classification = 'first.st',
                                           predictor      = 'natriuertic.peptide',
                                           model          = 'Natriuertic Peptide')
## # Mrproanp
biomarker$mrproanp <- dipep_glm(df = dipep,
                                classification = 'first.st',
                                predictor      = 'mrproanp',
                                model          = 'MR-proANP')

## Combine all three sets of tidied output from each model
biomarker$tidied <- rbind(biomarker$prothombin.time$tidied,
                          biomarker$aprothombin$tidied,
                          biomarker$clauss.fibrinogen$tidied,
                          biomarker$ddimer.innovan$tidied,
                          biomarker$ddimer.elisa$tidied,
                          biomarker$thrombin.generation.lag.time$tidied,
                          biomarker$thrombin.generation.endogenous.potential$tidied,
                          biomarker$thrombin.generation.peak$tidied,
                          biomarker$thrombin.generation.time.to.peak$tidied,
                          biomarker$plasmin.antiplasmin$tidied,
                          biomarker$prothrombin.fragments$tidied,
                          biomarker$soluble.tissue.factor$tidied,
                          biomarker$troponin$tidied,
                          biomarker$natriuertic.peptide$tidied,
                          biomarker$mrproanp$tidied)
biomarker$glance <- rbind(biomarker$prothombin.time$glance,
                          biomarker$aprothombin$glance,
                          biomarker$clauss.fibrinogen$glance,
                          biomarker$ddimer.innovan$glance,
                          biomarker$ddimer.elisa$glance,
                          biomarker$thrombin.generation.lag.time$glance,
                          biomarker$thrombin.generation.endogenous.potential$glance,
                          biomarker$thrombin.generation.peak$glance,
                          biomarker$thrombin.generation.time.to.peak$glance,
                          biomarker$plasmin.antiplasmin$glance,
                          biomarker$prothrombin.fragments$glance,
                          biomarker$soluble.tissue.factor$glance,
                          biomarker$troponin$glance,
                          biomarker$natriuertic.peptide$glance,
                          biomarker$mrproanp$glance)
## Combine all predicted
biomarker$predicted <- rbind(biomarker$prothombin.time$predicted,
                             biomarker$aprothombin$predicted,
                             biomarker$clauss.fibrinogen$predicted,
                             biomarker$ddimer.innovan$predicted,
                             biomarker$ddimer.elisa$predicted,
                             biomarker$thrombin.generation.lag.time$predicted,
                             biomarker$thrombin.generation.endogenous.potential$predicted,
                             biomarker$thrombin.generation.peak$predicted,
                             biomarker$thrombin.generation.time.to.peak$predicted,
                             biomarker$plasmin.antiplasmin$predicted,
                             biomarker$prothrombin.fragments$predicted,
                             biomarker$soluble.tissue.factor$predicted,
                             biomarker$troponin$predicted,
                             biomarker$natriuertic.peptide$predicted,
                             biomarker$mrproanp$predicted)


```

```{r child = 'biomarkers/biomarker_summary.Rmd', eval = TRUE}
```

#### Logistic Regression

The point-estimate and 95% Confidence Intervals from univariable logistic regression are plotted and tabulated below.

```{r results_biomarker_regression_summary, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
to.sum <- dplyr::filter(biomarker$tidied, term != '(Intercept)') %>%
          dplyr::select(term, estimate, lci, uci, p.value)
ggplot(to.sum, aes(term, estimate, colour = term)) +
    geom_point() + geom_errorbar(aes(ymin = lci, ymax = uci)) +
    coord_flip() + geom_hline(yintercept = 0) +
    xlab('Predictor') + ylab('Estimate') +
    ggtitle('Point Estimate and 95% CI for Univariable Logistic Regression of Biomarkers') +
    theme_bw() + theme(legend.position = 'none')
## Redo subsetting, include temperature and O2 Saturation
to.sum <- dplyr::filter(biomarker$tidied, term != '(Intercept)') %>%
          dplyr::select(term, estimate, lci, uci, p.value)
names(to.sum) <- c('Term', 'Estimate', 'Lower CI', 'Upper CI', 'P-Value')
kable(to.sum,
      digits  = 3,
      caption = 'Point estimates, 95% CIs and p-values for Univariable Regression')
rm(to.sum)

```

##### ROC Curves

[Sensitivity and Specificity](https://en.wikipedia.org/wiki/Sensitivity_and_specificity) are not absolute since each individual is assigned a probability from the logistic regression model and it is then down to the investigator to decide what threshold ($0 < x < 1$ if not exponentiated) should be used to classify someone as having a Pulmonary Embolism.  A simple way of visualising the sensitivity and specificity for different thresholds is via a [Receiver Operating Characteristic Curve](https://en.wikipedia.org/wiki/Receiver_operating_characteristic) which plots the [false-positive rate](https://en.wikipedia.org/wiki/False_positive_rate) against the true positive rate.  The following graph shows the curves for the different univariable logistic regression models.

```{r results_biomarker_regression_roc, echo = FALSE, cache = FALSE, results = 'markup', eval = TRUE}
## This uses the geom_roc() ggplot2 extension from the ploROC package
## ROC for continuous variables
biomarker$roc.other <- dipep_roc(df      = biomarker$predicted,
                           to.plot = c('clauss.fibrinogen',
                                       'ddimer.innovan',
                                       'ddimer.elisa',
                                       'plasmin.antiplasmin',
                                       'soluble.tissue.factor',
                                       'troponin'),
                           title    = 'Other Biomarkers')
biomarker$roc.other$plot
biomarker$roc.thrombin <- dipep_roc(df      = biomarker$predicted,
                                    to.plot = c('aprothombin',
                                                'prothombin.time',
                                                'thrombin.generation.lag.time',
                                                'thrombin.generation.endogenous.potential',
                                                'thrombin.generation.peak',
                                                'thrombin.generation.time.to.peak',
                                                'prothrombin.fragments'),
                                    title    = 'Thrombin/Prothombin Biomarkers')
biomarker$roc.thrombin$plot
## Combine the AUC and print as table
rbind(biomarker$roc.other$plot.auc,
      biomarker$roc.thrombin$plot.auc) %>%
    dplyr::select(-c(x, y)) %>%
    kable(digits = 3,
          caption = 'Area Under the Curve (AUC) statistics of ROC curves for Biomarkers')

```
