##### Continuous Variables

```{r results_rpart_continuous, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
## Repeat using continuous variables
rpart.continuous <- dipep_rpart(df             = dipep,
                          classification = 'first.st',
                          predictor      = c('age', 'smoking', 'temperature', 'bp.diastolic', 'bp.systolic',
                                             'o2.saturation', 'respiratory.rate', 'bmi',
                                             'pregnancies.under', 'pregnancies.over', 'prev.preg.problem',
                                             'presenting.features.pleuritic',
                                             'presenting.features.non.pleuritic', 'presenting.features.sob.exertion',
                                             'presenting.features.sob.rest', 'presenting.features.haemoptysis',
                                             'presenting.features.cough', 'presenting.features.syncope',
                                             'presenting.features.palpitations', 'presenting.features.other',
                                             'surgery', 'cesarean', 'thromb.event',
                                             'thromboprophylaxis', 'thrombosis', 'preg.post', 'num.fetus'),
                          exclude.non.recruited = TRUE,
                          exclude.dvt           = TRUE,
                          exclude.missing       = TRUE,
                          legend                = FALSE,
                          threshold             = 0.5,
                          rpart.opts.method     = 'class',
                          rpart.opts.minsplit   = 4,
                          rpart.opts.minbucket  = 2,
                          rpart.opts.cp         = -1)

```

This section shows the results from applying recursive partitioning to raw continuous variables, allowing the recursive partitioning algorithm to determine the optimal split at each point.  Leave One Out Cross-Validation (LOOCV) is performed automatically by the `rpart` package at each partition and the resulting estimates used in summarising and prunning the tree.

The [dendrogram](https://en.wikipedia.org/wiki/Dendrogram) below shows the full, over-fitted.  As its over-fitted there are a lot of splits and the graph is barely legible.




```{r results_rpart_continuous_plot, echo = FALSE, cache = FALSE, fig_width = 15, fig_height = 10, eval = TRUE}
prp(rpart.continuous$rpart.full,
    type        = prp.opts$type,
    extra       = prp.opts$extra,
    box.palette = prp.opts$box.palette,
    yesno       = prp.opts$yesno,
    branch      = prp.opts$branch,
    varlen      = prp.opts$varlen,
    faclen      = prp.opts$faclen)

```

This model, because it was forced to fit a full model that categorised everyone, is over-fitted, meaning its generalisability and application in individuals not in the cohort will be poor.  To improve the generalisability of the model we now prune the tree by selecting a more permisive value for the complexity parameter (`cp`).  It is recommended that a decision tree is pruned using the Complexity Parameter that corresponds to the minimum cross-validated error (`xerror` in the table below) (@hastie2003 Section 7.10 pg244).  The Complexity Parameter (`cp`) along with associated cross-validated error (`xerror`) is tabulated below and a plot of the two parameters is shown.

```{r results_rpart_continuous_output, echo = FALSE, cache = FALSE, results = 'rmarkdown', eval = TRUE}
rpart.continuous$rpart.full.cp %>%
    kable(caption = 'Summary table for over-fitted full model.',
          col.names = c('Complexity Parameter', 'Splits', 'Relative Error', 'Cross-Validated Error', 'Cross-Validated SD'))
plotcp(rpart.continuous$rpart.full)

```

The Complexity Parameter (CP) at the step/number of splits (`r rpart.continuous$rpart.full.splits.min`) that corresponds to the minimum cross-validated error is `r rpart.continuous$rpart.full.cp.min`.

```{r results_rpart_continuous_prune, echo = FALSE, cache = FALSE, fig_width = 15, fig_height = 10, results = 'rmarkdown', eval = TRUE}
prp(rpart.continuous$pruned.min,
    type        = prp.opts$type,
    extra       = prp.opts$extra,
    box.palette = prp.opts$box.palette,
    yesno       = prp.opts$yesno,
    branch      = prp.opts$branch,
    varlen      = prp.opts$varlen,
    faclen      = prp.opts$faclen)

```

We now need to calculate the sensitivity and specificity.  There is no single value for either of these metrics since individuals have a predicted probability of classification in the range of $0 < p < 1$ rather than a binary classification.  One approach to viewing the trade-off of the two is to plot the Specificity v's the Sensitivity in what is known as a [Receiver Operating Characteristics (ROC) Curve](https://en.wikipedia.org/wiki/Receiver_operating_characteristic) and calculating the [Area Under the Curve (AUC)](https://en.wikipedia.org/wiki/Receiver_operating_characteristic#Area_under_the_curve) which captures the probability of correctly classifying true positives compared to true negatives.


```{r results_rpart_continuous_roc_min, echo = FALSE, cache = FALSE, fig_width = 10, fig_height = 10, warnings = FALSE, eval = TRUE}
rpart.continuous$roc.min$plot

```

The question arises though whether it is possible to utilise a simpler, more parsimonious tree with less splits, yet still retain the ability to make useful and accurate predictions.  To this end the ROC curve for each step/split in the recursive partitioning process are plotted below and a table of the performance statistics is provided for each step.

**IMPORTANT** - Dichotomising individuals predicted probability of disease is required in order to calculate the Sensitivity, Specificity point estimates nor the Positive or Negative Predictive Value.  For now a cut-point of `p = 0.5` has been used, but this is unlikely to be optimal for any of the trees.

```{r results_rpart_continuous_roc_all, echo = FALSE, cache = FALSE, fig_width = 10, fig_height = 10, warnings = FALSE, eval = TRUE}
rpart.continuous$roc.all$plot
rpart.continuous$roc.all$summary.stats %>%
    kable(caption = paste0('Predictive statistics fo sequential splits of Recursive Partitioning using a cut point of p = ',
                           rpart.continuous$threshold,
                           ','))

```

```{r results_rpart_continuous_roc_animate, echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.show = 'animate', eval = TRUE}
## Animation of ROC curve
ani.record(reset = TRUE)
par(bg = 'white')
splits <- dplyr::select(rpart.continuous$predicted, term) %>%
         unique() %>% nrow()
for(i in seq(1:splits)){
    t <- dplyr::filter(rpart.continuous$predicted, term == i) %>%
         ggplot(aes(d = D, m = M)) +
         geom_roc() +
         ggtitle(paste0('ROC Curves for Recursive Partitioning split ', i)) +
        style_roc() + theme_bw()
    print(t)
    ani.record()
}
oopts = ani.options(interval = 0.5)
ani.replay()
rm(t)

```
