##### Continuous Variables

```{r results_rpart_continuous, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
## Repeat using continuous variables
model <- reformulate(response = 'first.st',
                     termlabels = c('age', 'smoking', 'temperature', 'bp.diastolic', 'bp.systolic',
                                    'o2.saturation', 'respiratory.rate', 'bmi',
                                    'pregnancies.under', 'pregnancies.over', 'prev.preg.problem',
                                    'presenting.features.pleuritic',
                                    'presenting.features.non.pleuritic', 'presenting.features.sob.exertion',
                                    'presenting.features.sob.rest', 'presenting.features.haemoptysis',
                                    'presenting.features.cough', 'presenting.features.syncope',
                                    'presenting.features.palpitations', 'presenting.features.other',
                                    'surgery', 'cesarean', 'thromb.event',
                                    'thromboprophylaxis', 'thrombosis', 'preg.post', 'num.fetus'))
## Test model
continuous <- filter(dipep, group %in% c('Diagnosed PE', 'Suspected PE'))
continuous.n.missing <- dplyr::filter(continuous, is.na(first.st)) %>% nrow()
continuous <- rpart(model,
                    data = continuous,
                    method = rpart.opts$method,
                    control = rpart.control(minsplit  = rpart.opts$minsplit,
                                            minbucket = rpart.opts$minbucket,
                                            ## xval      = nrow(continuous),
                                            cp        = rpart.opts$cp))

```

The [dendrogram](https://en.wikipedia.org/wiki/Dendrogram) below shows the full, over-fitted.  As its over-fitted there are a lot of splits and the graph is barely legible.




```{r results_rpart_continuous_plot, echo = FALSE, cache = FALSE, fig_width = 15, fig_height = 10, eval = TRUE}
prp(continuous,
    type        = prp.opts$type,
    extra       = prp.opts$extra,
    box.palette = prp.opts$box.palette,
    yesno       = prp.opts$yesno,
    branch      = prp.opts$branch,
    varlen      = prp.opts$varlen,
    faclen      = prp.opts$faclen)

```

This model, because it was forced to fit a full model that categorised everyone, is over-fitted, meaning its generalisability and application in individuals not in the cohort will be poor.  To improve the generalisability of the model we now prune the tree by selecting a more permisive value for the complexity parameter (`cp`).  It is recommended that a decision tree is pruned using the Complexity Parameter of the smallest tree within one standard deviation of the smallest reported `xerror` (@hastie2003 Section 7.10 pg244).  The Complexity Parameter (`cp`) is plotted below for each split of the over-fitted full tree.

```{r results_rpart_continuous_output, echo = FALSE, cache = FALSE, results = 'rmarkdown', eval = TRUE}
printcp(continuous)
plotcp(continuous)

```

The horizontal dashed line shows the threshold for selecting the Complexity Parameter to prune the tree, and a value corresponding to the first point **below** this line is selected and applied to the data.

```{r results_rpart_continuous_prune, echo = FALSE, cache = FALSE, fig_width = 15, fig_height = 10, results = 'rmarkdown', eval = TRUE}
## Selecting cp for pruning...
## https://stats.stackexchange.com/questions/122333/interpreting-rpart-output-for-decision-trees?rq=1
cp.table <- categorical$cptable %>%
            as.data.frame() %>%
            mutate(mean = mean(xerror))
cp <- filter(cp.table, CP < mean)[1,1] / 10
continuous_prune <- prune(continuous, cp = cp)
printcp(continuous_prune,
        digits = printcp.opts$digits)
prp(continuous_prune,
    type        = prp.opts$type,
    extra       = prp.opts$extra,
    box.palette = prp.opts$box.palette,
    yesno       = prp.opts$yesno,
    branch      = prp.opts$branch,
    varlen      = prp.opts$varlen,
    faclen      = prp.opts$faclen)

```

We now need to calculate the sensitivity and specificity.  There is no single value since the cut-point for classifying can vary depending on the complexity value we wish to use, i.e. do we favour sensitivity over specificity or vice-versa.  One approach to viewing the trade-off of the two is to plot the Specificity v's the Sensitivity in what is known as a [Receiver Operating Characteristics (ROC) Curve](https://en.wikipedia.org/wiki/Receiver_operating_characteristic).

```{r results_rpart_continuous_roc, echo = FALSE, cache = FALSE, fig_width = 10, fig_height = 10, warnings = FALSE, eval = TRUE}
## .predict <- predict(continuous_prune, type = 'prob')
## .predicted <- prediction(.predict[,2] %>% as.vector(), continuous_prune$y)
## pred.obs <- cbind(.predict[,2] %>% as.vector(), continuous_prune$y) %>% as.data.frame()
pred.obs <- cbind(predict(continuous_prune, type = 'prob')[,2],
                  continuous_prune$y) %>%
            as.data.frame()
names(pred.obs) <- c('predicted', 'obs')
roc <- ggplot(pred.obs, aes(d = obs, m = predicted)) +
       geom_roc(n.cuts = 10) + style_roc() +
       ggtitle(paste0('ROC Curve for Pruned Continuous Tree (CP = ', round(cp, 5), ')'))
    ## Calculate AUC and add to plot
roc + annotate('text', x = 0.75, y = 0.25,
               label = paste0('AUC = ', round(calc_auc(roc)$AUC, 3)))

```

The full summary of the pruned tree is provided.  The `r continuous.n.missing` `observations deleted due to missingness` are those classified as `exclude` rather than to a disease status and not because of missing observations in the predictor variables.

```{r results_rpart_continuous_summary, echo = FALSE, cache = FALSE, results = 'rmarkdown', eval = TRUE}
summary(categorical_prune)

```
