##### Staged Models

When a person presents at hospital or Accident & Emergency the amount of information available to the triaging clinician will be variable.  Some patients may be fully aware and able to answer questions, whilst others may be unconcious.  To this end a sensible strategy is to develop a series of models based on available information, starting with physiological variables that will be available to all, then augmenting it with information that may be available from a persons medical records and assays from putative biomarkers before finally including responses to the questions included in this study.

```{r results_rpart_staged_physiology, echo = FALSE, cache = FALSE, results = 'hide', eval = TRUE}
## Repeat using continuous variables
model <- reformulate(response = 'first.st',
                     termlabels = c('age', 'temperature', 'bp.diastolic', 'bp.systolic',
                                    'o2.saturation', 'respiratory.rate', 'bmi', 'num.fetus'))
## Test model
physiology_continuous <- rpart(model,
                               data = filter(dipep, group %in% c('UKOSS', 'Suspected PE')),
                               method = rpart.opts$method,
                               minsplit = rpart.opts$minsplit,
                               minbucket = rpart.opts$minbucket,
                               cp = rpart.opts$cp)    ## NB - Make sure 'pe' is a factor!

```

```{r results_rpart_stage_physiology_output, echo = FALSE, cache = FALSE, results = 'rmarkdown', eval = TRUE}
printcp(physiology_continuous,
        digits = printcp.opts$digits)
plotcp(physiology_continuous)

```
The positive response to the split is always on the left-hand side of a node, the numbers in the boxes

```{r results_rpart_stage_physiology_plot, echo = FALSE, cache = FALSE, fig_width = 15, fig_height = 10, eval = TRUE}
prp(physiology_continuous,
    type        = prp.opts$type,
    extra       = prp.opts$extra,
    box.palette = prp.opts$box.palette,
    yesno       = prp.opts$yesno,
    branch      = prp.opts$branch,
    varlen      = prp.opts$varlen,
    faclen      = prp.opts$faclen)

```



In addition to the problem described for the categorical tree whereby overfitting arises due to forcing a fully fitted tree which then needs trimming, continuousy fitted partition trees also tend to be over-fitted, which makes their generalisability and utility in other, as yet unobserved datasets, severly limited because cut-points are based on the observed data which is only a sample of the target population.  To this end the fitted trees are again pruned to avoid this.  It is recommended that a decision tree is pruned using the Complexity Parameter of the smallest tree within one standard deviation of the smallest reported `xerror` (@hastie2003 Section 7.10 pg244).

```{r results_rpart_stage_physiology_prune, echo = FALSE, cache = FALSE, fig_width = 15, fig_height = 10, results = 'rmarkdown', eval = TRUE}
cp <- 0.00000
physiology_continuous_prune <- prune(physiology_continuous, cp = cp)
printcp(physiology_continuous_prune)
prp(physiology_continuous_prune,
    type        = prp.opts$type,
    extra       = prp.opts$extra,
    box.palette = prp.opts$box.palette,
    yesno       = prp.opts$yesno,
    branch      = prp.opts$branch,
    varlen      = prp.opts$varlen,
    faclen      = prp.opts$faclen)

```
