#### Delphi - Specificity

The Delphi Consensus panel derived three scores, the version which seeks to maximise specificity has been applied to the data and is summarised below.
```{r results_existing_delphi.specificity, echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10, results = 'markdown', eval = TRUE}
## Summarise
delphi.specificity <- dipep_existing_sum(df                    = dipep,
                                 title                 = 'Delphi Specificity Score',
                                 exclude               = NULL,
                                 exclude.non.recruited = TRUE,
                                 exclude.dvt           = TRUE,
                                 exclude.missing       = TRUE,
                                 first.st, delphi.specificity.pe, delphi.specificity)
## Plots
delphi.specificity$bar.chart
delphi.specificity$likert.plot
## Tables
kable(delphi.specificity$summary.table,
      caption = 'Summary of Delphi Specificity Score',
      digits = 3)
kable(delphi.specificity$table,
      digits  = 3,
      caption = 'Pulmonary Embolism status compared to predicted status based on Delphi Specificity Score.')
kable(delphi.specificity$performance.table,
      digits  = 3,
      caption = 'Performance indicators for the Delphi Specificity Score for Pulmonary Embolism applied retrospectively to the DiPEP data.')

```

The Delphi Specificity Score has also been analysed using the calculated delphi.specificitys rather than dichotomisation, the ROC curve below shows its performance treating the Delphi Specificity Score as a categorical variable.

```{r results_existing_delphi.specificity_extra, echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10, results = 'markdown', eval = TRUE}
delphi.specificity$roc.cat.plot

```

Whilst the ROC curve below shows its performance treating the Delphi Specificity Score as a continuous variable.

```{r results_existing_delphi.specificity_extra2, echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10, results = 'markdown', eval = TRUE}
delphi.specificity$roc.con.plot

```
