#### PERC Score

The PERC Score for study participants (@kline2004) is summarised below.  It should be noted that the PERC score is designed to be used when a diagnosis of PE is being considered but the risk is low (as described in the [online calculator](http://www.mdcalc.com/perc-rule-pulmonary-embolism/)).  A PERC Score $>= 1$ is taken as indicative of PE.
```{r results_existing_perc, echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10, results = 'markdown', eval = TRUE}
## Summarise
perc <- dipep_existing_sum(df                    = dipep,
                                 title                 = 'PERC Score',
                                 exclude               = NULL,
                                 exclude.non.recruited = TRUE,
                                 exclude.dvt           = TRUE,
                                 exclude.missing       = TRUE,
                                 first.st, perc.pe, perc)
## Plots
perc$bar.chart
perc$likert.plot
## Tables
kable(perc$summary.table,
      caption = 'Summary of PERC Score',
      digits = 3)
kable(perc$table,
      digits  = 3,
      caption = 'Pulmonary Embolism status compared to predicted status based on PERC Score.')
kable(perc$performance.table,
      digits  = 3,
      caption = 'Performance indicators for the PERC Score for Pulmonary Embolism applied retrospectively to the DiPEP data.')

```

The PERC Score has also been analysed using the calculated percs rather than dichotomisation, the ROC curve below shows its performance treating the PERC Score as a categorical variable.

```{r results_existing_perc_extra, echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10, results = 'markdown', eval = TRUE}
perc$roc.cat.plot

```

Whilst the ROC curve below shows its performance treating the PERC Score as a continuous variable.

```{r results_existing_perc_extra2, echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10, results = 'markdown', eval = TRUE}
perc$roc.con.plot

```
