#### Wells Score (Strict)

The Wells Score (@wells2001) is summarised below.  An [online calculator](https://www.mdcalc.com/wells-criteria-pulmonary-embolism) is available.  A score $> 4$ is taken as indicative of PE.

**NB** - Permissive means that for the item "*Pulmonary embolism is the most or equally likely diagnosis*" that "*Possibly PE*" have been excluded.
```{r results_existing_wells_strict, echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10, results = 'markdown', eval = TRUE}
## Summarise
wells.strict <- dipep_existing_sum(df                    = dipep,
                                 title                 = 'Wells Score (Strict)',
                                 exclude               = NULL,
                                 exclude.non.recruited = TRUE,
                                 exclude.dvt           = TRUE,
                                 exclude.missing       = TRUE,
                                 first.st, wells.strict.pe, wells.strict)
## Plots
wells.strict$bar.chart
wells.strict$likert.plot
## Tables
kable(wells.strict$summary.table,
      caption = 'Summary of Wells Score (Strict)',
      digits = 3)
kable(wells.strict$table,
      digits  = 3,
      caption = 'Pulmonary Embolism status compared to predicted status based on Wells Score (Strict).')
kable(wells.strict$performance.table,
      digits  = 3,
      caption = 'Performance indicators for the Wells Score (Strict) for Pulmonary Embolism applied retrospectively to the DiPEP data.')

```

The Wells Score (Strict) has also been analysed using the calculated wells.stricts rather than dichotomisation, the ROC curve below shows its performance treating the Wells Score (Strict) as a categorical variable.

```{r results_existing_wells_strict_extra, echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10, results = 'markdown', eval = TRUE}
wells.strict$roc.cat.plot

```

Whilst the ROC curve below shows its performance treating the Wells Score (Strict) as a continuous variable.

```{r results_existing_wells_strict_extra2, echo = FALSE, cache = FALSE, warning = FALSE, message = FALSE, fig.height = 10, fig.width = 10, results = 'markdown', eval = TRUE}
wells.strict$roc.con.plot

```
